N-WASP-dependent branched actin polymerization attenuates B-cell receptor signaling by increasing the molecular density of receptor clusters

Version 1

Abstract

Abstract

Antigen-induced B-cell receptor (BCR) signaling is critical for initiating and regulating B-cell activation. The actin cytoskeleton plays essential roles in BCR signaling. Upon encountering cell-surface antigens, actin-driven B-cell spreading amplifies signaling, while B-cell contraction following spreading leads to signal attenuation. However, the mechanism by which actin dynamics switch BCR signaling from amplification to attenuation is unknown. Here, we show that Arp2/3-mediated branched actin polymerization is required for B-cell contraction. Contracting B-cells generate centripetally moving actin foci from lamellipodial F-actin networks in the B-cell plasma membrane region contacting antigen-presenting surfaces. Actin polymerization driven by N-WASP, but not WASP, generates these actin foci. N-WASP-dependent actin foci facilitate non-muscle myosin II recruitment to the contact zone to create actomyosin ring-like structures. Furthermore, B-cell contraction increases BCR molecular density in individual clusters, leading to decreased BCR phosphorylation. Increased BCR molecular density reduced levels of the stimulatory kinase Syk, the inhibitory phosphatase SHIP-1, and their phosphorylated forms in individual BCR clusters. These results suggest that N-WASP-activated Arp2/3 generates centripetally moving foci and contractile actomyosin ring-like structures from lamellipodial networks, enabling contraction. B-cell contraction attenuates BCR signaling by pushing out both stimulatory kinases and inhibitory phosphatases from BCR clusters, providing novel insights into actin-facilitated signal attenuation.

Introduction

B-cell-mediated antibody responses are essential for eliminating invading pathogens. B-cell receptors (BCRs) expressed on the B-cell surface detect the presence of cognate antigens. The binding of antigen to the BCR leads to the activation of signaling cascades (Reth and Wienands 1997; Dal Porto et al. 2004; Kwak et al. 2019), which induce transcriptional programs that prepare B-cells for proliferation and differentiation (Kurosaki et al. 2010; Shlomchik et al. 2019; Wang et al. 2020). BCR signaling also induces rapid antigen internalization, processing, and presentation for T-cell recognition, which provides the second signal required for B-cell clonal expansion and differentiation to high-affinity antibody-secreting cells and memory B-cells (Song et al. 1995; Gitlin et al. 2014). BCR signaling is tightly regulated by various external and internal factors to activate antibody responses that are specific and also qualitatively and quantitatively matched to the encountered antigen.

Antigen-induced receptor reorganization activates BCRs at the B-cell surface. Antigen binding leads to BCR clustering at lipid rafts, which enables raft-resident kinases, such as the Src kinases Lyn and Fyn, to phosphorylate immunoreceptor tyrosine-based activation motifs (ITAMs) in the cytoplasmic domains of the BCR signaling subunit CD79a/b heterodimer (Reth 1994; Pierce 2002; Sohn et al. 2008). Doubly phosphorylated ITAMs recruit and activate spleen tyrosine kinase (Syk), which in turn activates multiple downstream signaling pathways, including phospholipase Cγ2 (PLCγ2), Bruton’s tyrosine kinase (Btk), Ras-GTPase, and phosphatidylinositol-3 kinase (PI3K), initiating signaling cascades (Kurosaki 2000; Dal Porto et al. 2004; Tanaka and Baba 2020). Signaling activation also induces the recruitment and activation of inhibitory phosphatases, such as SH2-containing tyrosine phosphatase-1 (SHP-1) and phosphatidylinositol-5 phosphatase-1 (SHIP-1), to BCR signaling complexes (Brauweiler et al. 2000; Gross et al. 2009; Franks and Cambier 2018). SHIP-1 and SHP-1 negatively regulate BCR signaling by inactivating the plasma membrane docking lipids for stimulatory kinases, such as Btk and Akt (Aman et al. 1998; Bolland et al. 1998) and dephosphorylating BCR and its downstream signaling molecules (Mizuno et al. 2000; Adachi et al. 2001), respectively. The interplay between the stimulatory kinases and the inhibitory phosphatases controls the balance of antibody responses against pathogens and self. Deficiencies in stimulatory kinases by mutations, such as Btk, cause X-linked agammaglobulinemia (XLA) (Kinnon et al. 1993), while deficiencies in the inhibitory phosphatases SHP-1 or SHIP-1 result in autoimmune diseases (Pao et al. 2007; Leung et al. 2013). However, the mechanisms by which BCR signaling attenuation is initiated and regulated remain elusive.

B-cells encounter both soluble and membrane-associated antigens in vivo. Membrane-associated antigens include antigens on antigen-presenting cells, like follicular dendritic cells in B-cell follicles or germinal centers, and pathogenic cells, like bacteria, parasites, and cancer cells (Batista and Harwood 2009; Depoil et al. 2009; Gonzalez et al. 2009; Cyster 2010). The binding of multi-valent soluble antigen and membrane-associated antigen with any valency induces dynamic reorganization of surface BCRs into microclusters, triggering BCR signaling. Subsequently, surface BCRs continue moving to the plasma membrane region contacting antigen-presenting surfaces or to one B-cell pole in the case of soluble antigen, which leads to the growth and merger of BCR microclusters and the formation of immunological synapses (Carrasco et al. 2004; Harwood and Batista 2010) or supra-molecular activation complexes (Unanue and Karnovsky 1973; Schreiner and Unanue 1977; Tolar et al. 2009b; Harwood and Batista 2010).

Multiple mechanisms have been proposed for signaling initiation by antigen-induced surface BCR reorganization. The binding of surface BCRs to membrane-associated antigen has been shown to induce a conformational change in the BCR extracellular domain, exposing a proximal membrane region of membrane IgM that promotes receptor clustering (Tolar et al. 2009a; Shen et al. 2019). Antigen-binding also changes the conformation of the BCR cytoplasmic domains from a closed to an open form, facilitating the recruitment of signaling molecules (Tolar et al. 2005). Alternatively, antigen-BCR interaction can increase the molecular spacing of BCRs in clusters, facilitating BCR interaction with signaling molecules (Yang and Reth 2010; Kläsener et al. 2014). The inhibitory phosphatases SHP-1 and SHIP-1 are also recruited to BCR clusters (Adachi et al. 2001; Seeley-Fallen et al. 2014). However, the mechanisms underlying phosphatase recruitment and its relationship with BCR signaling activation complexes are unknown.

The actin cytoskeleton is essential for antigen-induced BCR reorganization on the B-cell surface in response to both soluble and membrane-associated antigen (Harwood and Batista 2011; Liu et al. 2013b; Song et al. 2013; Hoogeboom and Tolar 2016). Early signaling of the BCR triggers transient actin depolymerization via Rap GTPase and its downstream target cofilin (Freeman et al. 2011), which disassembles the existing cortical actin network that confines the lateral movement of surface BCRs (Treanor et al. 2010). Following this transient depolymerization, BCR signaling activates rapid actin polymerization through the actin nucleation promoting factors Wiskott-Aldrich Syndrome Protein (WASP) and neuronal-WASP (N-WASP), modulating BCR mobility and leading to F-actin accumulation at BCR-antigen interaction sites (Liu et al. 2013a; Rey-Suarez et al. 2020). Actin polymerization and treadmilling in B-cells stimulated by soluble antigen drive surface BCRs to cluster and move to one pole of the B-cell, forming a BCR cap (Schreiner and Unanue 1977; Liu et al. 2012a). Upon interacting with membrane-associated antigen, B-cells organize actin into two dynamic structures. One treadmills outwards, driving B-cell membrane spreading and expanding the B-cell membrane region contacting the antigen-presenting surface (contact zone), which enables more BCRs to engage antigen (Bolger-Munro et al. 2019). The other creates retrograde flow towards the center of the B-cell contact zone, driving the centripetal movement and growth of BCR microclusters (Liu et al. 2012b). Together, these processes amplify BCR signaling (Batista et al. 2010; Harwood and Batista 2011). The extent of B-cell spreading and the amount of BCR-antigen complexes gathered in the contact zone depend on BCR binding affinity and the density of antigen on the membrane (Fleire et al. 2006). Subsequent to spreading, B-cells contract, reducing the contact area, which drives BCR microclusters to merge into central clusters to form immunological synapses (Fleire et al. 2006; Liu et al. 2013a).

The actin cytoskeleton closely interplays with BCR signaling. We have previously shown that mouse primary B-cells with Btk deficiency (Liu et al. 2011) or double knockouts of the actin nucleation promoting factors WASP and N-WASP (Liu et al. 2013a) fail to spread on antigen-presenting surfaces and establish stable interactions with membrane-associated antigen, drastically reducing BCR signaling. Btk can activate WASP and N-WASP through Vav, the guanine nucleotide exchange factor of Cdc42 and Rac and phosphatidylinositol-5 kinase that generates phosphatidylinositol-4,5-biphosphate (PI4,5P2) (Sharma et al. 2009; Padrick and Rosen 2010). Surprisingly, B-cell-specific knockout of N-WASP (cNKO) but not WASP germline knockout (WKO) enhances B-cell spreading, delays B-cell contraction, and inhibits the centralization of BCR clusters at the contact zone (Liu et al. 2013a). Consistent with these findings, Bolger-Munro et al. have shown that knockdown of the actin nucleation factor Arp2/3 downstream of WASP and N-WASP disrupts the dynamic actin reorganization induced by membrane-associated antigen required for BCR microcluster growth and merger (Bolger-Munro et al. 2019). Using B-cell-specific and germline knockouts, we showed that in addition to N-WASP, the actin motor non-muscle myosin IIA (NMIIA) (Seeley-Fallen et al. 2022) and the actin-binding adaptor protein Abp1 (Seeley-Fallen et al. 2014) are required for B-cell contraction and BCR central cluster formation. Finally, Wang et al. recently showed that in the presence of the adhesion molecule ICAM on the antigen-presenting surface, B-cells form contractile actomyosin arcs, driving centripetal movement of BCR clusters in the B-cell contact zone (Wang et al. 2022). Together, these findings indicate a critical role of different actin networks in B-cell contraction and BCR signaling.

Our previously studies demonstrate that B-cell contraction is critical for BCR signaling attenuation. Delay and inhibition of B-cell contraction through deficiencies of the actin regulators N-WASP, Abp1, or NMIIA, prolongs and/or increases BCR signaling by enhancing the activation of stimulatory kinases and suppressing the activation of inhibitory phosphatases, which elevates the production of autoantibody levels in mice (Liu et al. 2013a; Seeley-Fallen et al. 2014; Seeley-Fallen et al. 2022). N-WASP and NMIIA are not known to interact with kinases and phosphatases directly. The growth, merger, and centralization of antigen-BCR complexes at the B-cell contact zone during the B-cell contraction phase are associated with the reduced BCR signaling capability (Liu et al. 2013a). These findings suggest that B-cell contraction is one of the mechanisms for inducing BCR signaling attenuation. However, how the actin cytoskeleton facilitates the transition of the spreading to contraction phase and how B-cell contraction switches BCR signaling from amplification to attenuation is unknown.

This study explores the mechanisms by which the actin cytoskeleton remodels from spreading lamellipodia to contractile structures and by which B-cell contraction suppresses BCR signaling. Our results show that the contractile actomyosin structures responsible for B-cell contraction originate from branched actin at spreading lamellipodia. N-WASP/Arp2/3-mediated actin polymerization prolongs the lifetime of the lamellipodial actin structures, enables NMIIA recruitment, and drives their movement to the center of the B-cell contact zone. B-cell contraction increases the molecular density within individual BCR-antigen clusters, which promotes the disassociation of both the stimulatory kinase Syk and the inhibitory phosphatases SHIP-1 from BCR clusters, leading to signal attenuation. Our study reveals a new mechanism underlying BCR signal downregulation.

Results

Arp2/3, activated by N-WASP but not WASP, is required for B-cell contraction

Arp2/3-generated branched F-actin is known to drive lamellipodial expansion for B-cell spreading (Bolger-Munro et al. 2019). However, whether branched F-actin is involved in the subsequent contraction phase is unknown. To address this, we perturbed the polymerization of branched F-actin using the Arp2/3 inhibitor CK-666 (50 µM) while using its inactive derivative CK-689 as a control. Pre-warmed splenic B-cells from WT C57BL/6 mice were incubated with monobiotinylated Fab’ fragment of anti-mouse IgM+G attached to planar lipid bilayers (Fab’-PLB) by biotin-streptavidin interaction and imaged live at 37°C using interference reflection microscopy (IRM). The contact area of B-cells treated with CK-689 rapidly increased upon contacting Fab’-PLB and reached a maximum at ≥0.5 min after the initial contact (Figure 1A, Figure 1-figure supplement 1, and Figure 1-Video 1A). Following maximal spreading, most B-cells reduced the area of their contact zone, indicating contraction (Figure 1A, Figure 1-figure supplement 1, and Figure 1-Video 1A). We classified a B-cell as contracting if its contact zone area reduced by ≥5% for at least 10 sec after reaching a maximum value. Based on the average timing for B-cell maximal spreading, we treated B-cells with CK-666 at the beginning of the incubation (Time 0), before B-cell spreading initiation, or at 2 min, when all B-cells had already spread. The effectiveness of CK-666 was detected by reduced Arp2/3 staining in the contact zone (Figure 1-figure supplement 2). As expected, CK-666 treatment at 0 but not 2 min reduced the kinetics of B-cell spreading (Figure 1-figure supplement 3). Importantly, CK-666 treatment at 0 and 2 min both significantly reduced the percentage of B-cells undergoing contraction (Figure 1A-C and Figure 1-Video 1A). The inhibitory effect of CK-666 on B-cell contraction, particularly CK-666 treatment after B-cell spreading, suggests that Arp2/3-mediated branched actin polymerization is required for B-cell contraction.

Arp2/3, activated by N-WASP but not WASP, is required for B-cell contraction.

Splenic B-cells were incubated with planar lipid bilayers coated with monobiotinylated Fab’ fragment of goat anti-mouse IgG+M (Fab’-PLB) in the absence and presence of various inhibitors and imaged live at 37°C by interference reflection microscopy (IRM). The B-cell plasma membrane area contacting Fab’-PLB (B-cell contact zone) was measured using IRM images and custom MATLAB scripts. (A) Representative IRM images of splenic B-cells from C57BL/6 mice treated with CK-689 or CK-666 (50 µM) before (0 min) and after maximal spreading (2 min). (B) Representative plots of the B-cell contact area versus time from one contracting cell and one non-contracting cell. (C) Percentages (±SEM) of B-cells that underwent contraction after treatment with CK-666 or CK-689. (D) Representative IRM images of splenic B-cells from C57BL/6 mice treated with DMSO or Wiskostatin (Wisko, 10 µM) 10 min before and during incubation with Fab’-PLB. (E) Percentages (±SEM) of B-cells that underwent contraction after treatment with Wisko or DMSO. (F) Representative IRM images of splenic B-cells from flox control and B-cell-specific N-WASP knockout (cNKO) mice. (G) Percentages (±SEM) of cNKO or flox control B-cells that underwent contraction. (H) Representative IRM images of splenic B-cells from WT or WASP knockout mice (WKO). (I) Percentages (±SEM) of WKO or WT B-cells that underwent contraction. Data were generated from three independent experiments, with ∼25 cells per condition, per experiment. Scale bar, 2 µm. *p <0.05, ***p<0.001, by paired student’s t-test.

Figure supplement 1. B-cells spread and contract on Fab’-coated-planar lipid bilayers.

Figure supplement 2. CK-666 significantly decreases Arp2/3 recruitment to the B-cell contact zone.

Figure supplement 3. CK-666 treatment before but not after maximal B-cell spreading decreases the spreading kinetics.

Figure supplement 4. Wiskostatin treatment inhibits N-WASP activation while enhancing WASP activation in B-cells.

Figure 1–Video 1. Effects of CK-666, Wiskostatin, conditional N-WASP knockout, and WASP knockout on B-cell contraction.

WASP and N-WASP are actin nucleation-promoting factors upstream of Arp2/3 that are expressed in B-cells (Padrick and Rosen 2010). To determine if either or both were responsible for activating Arp2/3 for B-cell contraction, we utilized the N-WASP inhibitor wiskostatin (Wisko), and splenic B-cells from B-cell-specific N-WASP knockout mice (cNKO) and germline WASP knockout (WKO) mice (Westerberg et al. 2012; Liu et al. 2013a). Wisko has been shown to inhibit N-WASP activation while enhancing WASP activation in B-cells (Figure 1-figure supplement 4) (Liu et al. 2013a). We found that both Wisko (10 µM) (Figure 1D and E and Figure 1-Video 1B) and cNKO (Figure 1F and G and Figure 1-Video 1C), but not WKO (Figure 1H and I and Figure 1-Video 1D), significantly reduced the percentage of B-cells undergoing contraction, compared to the vehicle, flox, or WT controls. These results suggest that N-WASP- but not WASP-activated Arp2/3 mediates branched actin polymerization for B-cell contraction.

Arp2/3, downstream of N-WASP, generates inner F-actin foci, driving B-cell contraction

To understand how Arp2/3 drives B-cells to transition from spreading to contraction, we identified F-actin structures associated with contracting B-cells that were sensitive to CK-666 treatment. We visualized F-actin by phalloidin staining and compared F-actin organization in the contact zone of B-cells at the spreading (2 min) and contraction (4 min) phases using TIRF. While B-cells in both spreading and contraction phases exhibited phalloidin staining outlining the contact zone (Fig. 2A, green arrows), only B-cells in the contracting phase showed interior phalloidin patches brighter than the phalloidin staining at the periphery of the contact zone (Figure 2A, purple arrows). These F-actin patches were organized into a ring-like structure and resided ∼1 μm behind the spreading front, surrounding an F-actin-poor center (Figure 2A, purple arrows). Here, we refer these F-actin patches as inner F-actin foci. We identified inner F-actin foci based on whether their peak fluorescence intensity (FI) was ≥2 fold of the mean fluorescence intensity (MFI) of phalloidin in the no-foci area, had diameters of ≥250 nm, and were located 1 µm away from the edge of the contact zone. We found that such inner F-actin foci were detected in >60% of B-cells in the contracting phase (4 min) but only in <20% of B-cells in the spreading phase (2 min) (Figure 2B). CK-666 treatment at 0 min, which inhibited B-cell contraction, significantly reduced the percentage of B-cells showing inner F-actin foci at 4 min but not at 2 min (Figure 2B). CK-666 treatment did not affect the phalloidin staining outlining the contact zone (Figure 2A). Similarly, the percentage of cNKO B-cells showing inner F-actin foci was drastically reduced at 4 min but not at 2 min (Figure 2C). These results suggest that the formation of these inner F-actin foci is associated with B-cell contraction.

Arp2/3, downstream of N-WASP, generates inner F-actin foci, driving B-cell contraction.

(A-C) WT splenic B-cells were treated with CK-689 or CK-666 (50 µM) during incubation with Fab’-PLB (A and B), and flox control and cNKO B-cells were incubated with Fab’-PLB at 37°C (C). Cells were fixed at 2 and 4 min, permeabilized, stained for F-actin with phalloidin, and analyzed using TIRF. Shown are representative TIRF images of phalloidin staining in the contact zone of CK-689 and CK-666-treated B-cells (A, left panels) and fluorescence intensity (FI) profiles of phalloidin staining along a line crossing cells (A, right panels). Green arrows indicate lamellipodial F-actin, and purple arrows indicate inner F-actin foci forming a ring-like structure. Percentages of cells (per image) (±SEM) with inner F-actin foci forming ring-like distribution among CK-689-versus CK-666-treated cells (B) and flox control versus cNKO B-cells (C) before (2 min) and after (4 min) contraction were determined by visual inspection of phalloidin FI line-profiles across the B-cell contact zones. Data were generated from 3 independent experiments with 5 images per condition per experiment and ∼15 cells per image. (D-G) Inner F-actin foci were identified by their diameter (≥250 nm), peak FI (≥2 fold of no foci area, and location (1 µm away from the outer edge) and quantified as the number per cell using TIRF images. (D) Shown are representative images of splenic B-cells from LifeAct-GFP-expressing mice treated with CK-689 or CK-666 from 0 min during incubation with Fab’-PLB at 37°C (top) and the average number (±SEM) of inner LifeAct-GFP foci per cell (bottom) at 2 min. (E) LifeAct-GFP B-cells were treated with CK-666 at 2 min. Shown are representative TIRF images of LifeAct-GFP in the contact zone of B-cells (top) and the average number (±SEM) of inner LifeAct-GFP foci (bottom) in the same cell 10s before and 20s after CK-666 treatment. (F) Shown are representative TIRF images of phalloidin-staining in the contact zone of flox control and cNKO B-cells after incubating with Fab’-PLB for 2 min (top) and the average number (±SEM) of inner F-actin foci per cell (bottom). (H) Shown are representative TIRF images of WT and WKO B-cells expressing LifeAct-GFP incubated with Fab’-PLB for 2 min and the average number (±SEM) of inner F-actin foci per cell (bottom). Data points represent individual cells from three independent experiments with 10 (D, F, and G) or 6 (E) cells per condition per experiment. Scale bar, 2 µm. ** p <0.01, *** p<0.001, by non-parametric student’s t-test.

Figure 2-Video 1. Effects of CK-666 and WKO on F-actin foci formation.

We further quantified the number of inner F-actin foci in individual B-cells from mice expressing the LifeAct-GFP transgene (Riedl et al. 2010) (Figure 2D, E, and G), which allowed us to monitor F-actin reorganization using live-cell imaging (Figure 2-Video 1), or using phalloidin staining in flox control and cNKO B-cells (Figure 2F). Consistent with the results with phalloidin staining, CK-666 treatment at time 0 significantly reduced the number of inner F-actin foci in the contact zone (Figure 2D and Figure 1-Video 1A and B). When we followed the same B-cells before and after CK-666 treatment at 2 min, many of the inner F-actin foci formed before the treatment (1 min 50 sec) disappeared after the treatment (2 min 20 sec), significantly reducing the number of inner F-actin foci (Figure 2E). Similar to the CK-666 treatment, cNKO cells significantly reduced the number of inner F-actin foci in the contact zone, compared to flox controls (Figure 2F). In contrast, WKO, which does not affect B-cell contraction, did not significantly change the number of inner F-actin foci, compared to WT control B-cells (Figure 2G and Figure 2-Video 1C and D). Thus, N-WASP- but not WASP-activated Arp2/3 drives the formation and the maintenance of contraction-associated inner F-actin foci.

Inner F-actin foci are derived from lamellipodial actin networks supporting the spreading membrane

We next examined the formation of contraction-associated inner F-actin foci utilizing live-cell TIRF imaging of B-cells from mice expressing LifeAct-GFP. We generated kymographs along eight lines from the center of each contact zone using time-lapse images of LifeAct-GFP (Figure 3A and B and Figure 3-figure supplement 1). Analysis of these kymographs showed that most F-actin foci were first detected closely behind lamellipodial F-actin networks. Following maximal spreading, these F-actin foci moved centripetally while increasing in intensity, becoming inner F-actin foci, in cells transitioning from spreading to contraction (Figure 3B, top panel, and Figure 3-figure supplement 1). However, such centripetally moving F-actin foci were not detected in B-cells that did not undergo contraction (Figure 3B, bottom panel). We quantified the percentage of the eight kymographs from each cell that exhibited lamellipodia-derived inner F-actin foci and found, on average, that six out of eight kymographs from contracting cells showed lamellipodia-derived inner F-actin foci, compared to only one or two kymographs from non-contracting cells (Figure 3C). To examine the temporal relationship between the generation of lamellipodia-derived inner F-actin foci and contraction, we plotted the percentage of kymographs with lamellipodia-derived inner F-actin foci over time with the spreading to contracting transition time set as 0 (Figure 3D). We found that the percentage of kymographs showing lamellipodia-derived inner F-actin foci peaked at almost the same time when the spreading transitioned to contraction (Figure 3D), suggesting a close temporal relationship between the two events. Furthermore, the N-WASP inhibitor Wisko, but not WKO, significantly inhibited the formation of lamellipodia-derived inner F-actin foci (Figure 3E). Thus, inner F-actin foci originate from branched actin driven lamellipodia and form simultaneously with the transition of B-cell spreading to contraction.

Inner F-actin foci are originated from lamellipodia behind the spreading membrane.

Mouse splenic B-cells from LifeAct-GFP transgenic mice were treated with DMSO or Wisko (10 µM), imaged live using TIRF during incubation with Fab’-PLB at 37°C, and analyzed using kymographs generated by NIH ImageJ. (A) One frame of TIRF time-lapse images of LifeAct-GFP in the contact zone of B-cells treated with DMSO or Wisko. Lines indicate eight kymographs that were randomly generated from each cell. (B) Representative kymographs were generated from TIRF time-lapse images of LifeAct-GFP at the red line in (A). Top panel, a contracting cell. Arrows indicate the start of contraction with inner F-actin foci originating from lamellipodia. Bottom panel, a non-contracting cell. Lamellipodia-derived inner F-actin foci were identified by their LifeAct-GFP FI ≥2 fold of their nearby region, migrating out of the lamellipodial F-actin toward the center of the contact zone, and trackable for >8 sec. (C) Percentages (±SEM) of kymographs showing inner F-actin foci originating from lamellipodia per cell that did and did not undergo contraction. Data were generated from 3 independent experiments with ∼10 cells per condition per experiment. (D) A histogram of inner F-actin foci emerging (expressed as percentages of the total events, blue line) over time relative to the time of B-cell contraction (defined as 0 sec, indicated by a purple dash line and arrow). Data were generated from 5 independent experiments with ∼9 cells per condition per experiment. (E) Percentage (±SEM) of inner F-actin foci originated from lamellipodia observed in 8 randomly positioned kymographs of each DMSO- or Wisko-treated WT or untreated WKO B-cell. Data were generated from 3 independent experiments with ∼10 cells per condition per experiment. Scale bars, 2 µm. *** p<0.001, by non-parametric student’s t-test.

Figure supplement 1. Emerging of Inner F-actin foci from lamellipodia.

N-WASP-activated Arp2/3 generates inner F-actin foci by sustaining the lifetime and the centripetal movement of lamellipodial F-actin

We examined the mechanism by which N-WASP and Arp2/3 generate inner F-actin foci by measuring their relative lifetime and mobility using kymographs generated from TIRF time-lapse images of B-cells expressing LifeAct-GFP. Inner F-actin foci were identified as described above, and their tracks were manually determined (Figure 4A, black dashed lines). The time window in which an inner F-actin patch could be detected in a kymograph was measured as the relative lifetime, as actin foci could move away from the kymograph line or the TIRF evanescent field (Figure 4A, right panels). The distance each F-actin focus moved during its lifetime was used to calculate its speed (Figure 4A, right panels). Compared to CK-689-treated B-cells, CK-666 treatment at time 0 significantly reduced the relative lifetime and the centripetal speed of inner F-actin foci (Figure 4B-D). After B-cells were treated with CK-666 at 2 min (the average time for B-cells to reach the maximal spreading), the relative lifetime and the centripetal speed of inner F-actin foci were significantly lower than before the treatment in the same cell (Figure 4E-G, line-linked dots). Similarly, the N-WASP inhibitor Wisko significantly reduced the relative lifetime and the centripetal speed of inner F-actin foci (Figure 4H-J); however, WKO had no significant effect (Figure 4K-M). These results show that N-WASP and Arp2/3 mediated branched actin polymerization prolongs the lifetime of lamellipodia-derived F-actin foci and drives them to move inward in the B-cell contact zone.

N-WASP-activated Arp2/3 sustains the lifetime and the centripetal movement of inner F-actin foci.

LifeAct-GFP-expressing B-cells were incubated with or without various inhibitors and imaged live by TIRF during interaction with Fab’-PLB at 37°C. Three randomly positioned kymographs were generated for each cell using time-lapse images. (A) A representative kymograph from TIRF time-lapse images of a DMSO-treated B-cell (Left panels). Inner F-actin foci were identified as described in Figure 3, and those that emerged during the 60 sec window after maximal spreading (white rectangles in B) and can be tracked for ≥ 4 sec (dashed lines) in individual kymographs were analyzed. Relative lifetimes of inner F-actin foci were measured using the duration each focus could be detected in a kymograph. The relative distances traveled by the foci were measured using the displacement of each focus in a kymograph. Relative speed was calculated for each inner F-actin focus by dividing its relative distance by its relative lifetime (right panels). (B-D) B-cells were treated with CK-689 or CK-666 (50 µM) from the beginning of the incubation with Fab’-PLB (0 min). Shown are representative kymographs (B), relative lifetimes (C), and relative speed (D) of inner F-actin foci in CK-689-versus CK-666-treated B-cells. (E-G) B-cells were treated with CK-666 at maximal spreading (2 min). Shown is a representative kymograph of a CK-666-treated cell (E), relative lifetimes (F), and relative speeds (G) of inner F-actin foci in 30-sec windows before the inhibition and 10 sec after the inhibition in the same cells (linked by blue lines). (H-J) B-cells were treated with DMSO or Wisko (10 µM) 10 min before and during interaction with Fab’-PLB. Shown is a representative kymograph of a Wisko-treated B-cell (H), relative lifetime (I), and relative speed (J) of inner F-actin foci in DMSO versus Wisko-treated B-cells. (K-M) LifeAct-GFP-expressing WT and WKO B-cells were incubated with Fab’-PLB. Shown are a representative kymograph of a WKO B-cell (K), relative lifetime (L), and relative speed (M) of WT versus WKO B-cells. Data points represent the averaged values from inner F-actin foci in individual cells, with 3 kymographs per cell and ∼12 cells per condition per experiment from 3 independent experiments. Scale bar, 2 µm. * p <0.05, ** p <0.01, *** p<0.001, by non-parametric and paired student’s t-test.

Inner F-actin foci, generated by N-WASP-activated Arp2/3, facilitate NMII recruitment and reorganization into ring-like structures

As non-muscle myosin II (NMII) is required for B-cell contraction (Seeley-Fallen et al. 2022), we examined the relationship between the formation of inner F-actin foci and the recruitment and reorganization of NMII in the contact zone using TIRF imaging of B-cells from mice expressing a GFP-NMIIA transgene. Upon interacting with Fab’-PLB, the GFP-NMIIA MFI in the contact zone of untreated WT B-cells increased rapidly in the first minute and slowly afterward (Figure 5A and B and Figure 5-Video 1). Wiskostatin treatment significantly reduced the GFP-NMIIA MFI in the contact zone (Figure 5B) and its initial rate of increase (as determined by the slope of the GFP-NMIIA MFI increase at 0∼30 sec time window) (Figure 5C). Kymographs generated from time-lapse TIRF images of B-cells from mice expressing GFP-NMIIA and LifeAct-RFP showed that recruited NMIIA accumulated between lamellipodia and inner F-actin foci when the foci moved centripetally away from lamellipodia (Figure 5D, white arrow, and Figure 5-Video 1). Recruited NMIIA reorganized with inner F-actin foci to form a ring-like structure in the contact zone (Figure 5A, D, and E, and Figure 5-Video 1). The percentage of B-cells with NMIIA ring-like structures, visualized by immunostaining, increased over time as more B-cells underwent contraction (Figure 5E and F). Compared to flox controls, the percentage of cNKO B-cells with NMIIA ring-like structures was significantly decreased (Figure 5E and F). Wiskostatin treatment also reduced NMIIA recruitment and ring-like structure formation (Figure 5-Video 1). Surprisingly, the percentage of WKO B-cells with NMIIA ring-like structure was higher than that of flox control B-cells (Figure 5E and F). Thus, N-WASP and Arp2/3 mediated branched actin polymerization promotes the recruitment and the reorganization of NMII ring-like structures by generating inner F-actin foci in the contact zone.

Inner F-actin foci, generated by N-WASP-activated Arp2/3, facilitate NMII recruitment and ring-like structure formation.

(A-C) B-cells from mice expressing the GFP fusion of non-muscle myosin IIA (GFP-NMIIA) transgene were treated with DMSO or Wisko (10 µM) 10 min before and during incubation with Fab’-PLB. The B-cell contact zones were imaged live using TIRF. Shown are representative TIRF images of DMSO- and Wisko-treated B-cells at 30 sec (during spreading) and 2 min 30 sec (after maximal spreading) post landing (A, Scale bars, 2 µm), the averaged GFP-NMIIA MFI (±SEM) (B), and the initial rates of increasing (±SEM) of GFP-NMIIA in the contact zone (the slope of the initial GFP-NMIIA MFI versus time curves of individual cells) (C). Data points represent individual cells from 3 independent experiments with ∼6 cells per condition per experiment. * p <0.05, ***p<0.001, by Kolmogorov-Smirnov test (B) or non-parametric student’s t-test (C). (D) Primary B-cells from mice expressing both GFP-NMIIA and LifeAct-RFP transgenes were incubated with Fab’-PLB at 37°C and imaged live by TIRF. Shown are a representative TIRF image of a cell and a kymograph generated from time-lapse TIRF images at the yellow line. The purple arrow indicates the starting point of contraction, the white arrow GFP-NMIIA recruitment proximal to the spreading membrane, and the yellow arrow an F-actin (LifeAct-RFP) focus originating at the lamellipodia and moving away from the spreading membrane. (E, F) Primary B-cells from flox control, WKO, and cNKO mice were incubated with Fab’-PLB for indicated times. Cells were fixed, permeabilized, stained for NMII light chain, and imaged by IRM and TIRF. Shown are representative IRM and TIRF images (E) and percentages (±SD) of B-cells with the NMII ring-like structure in individual images (F), identified by visual inspection. The data were generated from 3 independent experiments with 5 images per condition per experiment. Scale bars, 2 µm. * p <0.05, ** p <0.01, *** p<0.001, by non-parametric student’s t-test.

Figure 5-Video 1. Wiskostatin treatment inhibits NMII ring-like structure formation.

B-cell contraction increases the BCR molecular density in individual clusters

To understand how B-cell contraction promotes BCR signaling attenuation, we examined the impact of B-cell contraction on the properties of BCR clusters. We first measured the MFI of AF546-Fab’ attached to PLB gathered by B-cells into the contact zone as an indication of the overall BCR molecular density. The clustering of AF546-Fab’ on PLB by B-cell binding reflects surface BCR clustering, as B-cell binding to transferrin (Tf)-tethered PLB does not cause surface BCRs to cluster and be phosphorylated (Figure 6-figure supplement 1) (Liu et al. 2011; Liu et al. 2013a). The MFI of AF546-Fab’ in the B-cell contact zone increased over time.

B-cell contraction increases the molecular density within BCR clusters.

Primary B-cells from WT mice were treated with CK-689 or CK-666 from the beginning of the incubation with AF546-Fab’-PLB (0 min) or at the maximal B-cell spreading (2 min) (A, D, E, H, I, N, O). WT B-cells were treated with DMSO or Wisko (10 µM) 10 min before and during the incubation with AF546-Fab’-PLB (B, F, J, P). B-cells from flox control and cNKO mice were incubated with AF546-Fab’-PLB (C, G, K, Q). The B-cell contact zones were imaged live by TIRF. (A-C) Representative time-lapse images at 30 sec (during B-cell spreading) and 2 min 30 sec (after maximal spreading) after cell landed. Scale bars, 2 µm. (D-G) The MFI of AF546-Fab’ in the contact zone was plotted over time. Purple rectangles indicate the contraction phase. (H-K) Rates of AF546-Fab’ MFI increases in the B-cell contact zone before and during contraction were determined by the slope of AF546-Fab’ MFI versus time plots. Data points represent individual cells and were generated from 3 independent experiments with 6-12 cells per experiment. * p <0.05, ** p <0.01, *** p<0.001, by Kolmogorov-Smirnov test (D-G) or paired student’s t-test (H-K). (L) A representative frame from a time-lapse of a CK-689-treated B-cell (left) shows AF546-Fab’ clusters 30 sec after contraction began, and enlarged time-lapse images (right) show a single AF546-Fab’ cluster over a 40-sec time window after contraction began. AF546 clusters were identified using the criteria: ≥250 nm in diameter, ≥1.1 fold of FI outside the B-cell contact zone, and trackable for ≥ 20 sec. Scale bars, 2 µm. (M) The peak FI of an AF546-Fab’ cluster was measured over time, and the increasing rate of AF546-Fab’ peak FI of this cluster was determined by the slope of the plot. (N-Q) The rates (±SEM) of increase in AF546-Fab’ peak FI in individual clusters were compared between during and after contraction (N), between B-cells treated with CK-689 and CK-666 from 0 min (O), between DMSO- and Wisko-treated B-cells (P), and between flox control and cNKO B-cells (Q) after B-cells reached maximal spreading. Data points represent individual cells, the averaged slopes of clusters detected in one B-cell, from 3 independent experiments with 6∼12 cells per condition per experiment. *p <0.05, ** p <0.01, ***p<0.001, by non-parametric student’s t-test.

Figure supplement 1. Fab’-PLB, but not Tf-PLB, induces BCR clustering and phosphorylation.

Figure supplement 2. Tracking and analyzing AF546-Fab’ clusters in the B-cell contact zone.

Figure 6-Video 1. Inhibition of B-cell contraction reduces the molecular density within BCR clusters.

Treatment with CK-666, Wisko, or cNKO all reduced the AF546-Fab’ MFI, particularly during the time window of B-cell contraction in controls (Figure 6A-G, purple rectangles, and Figure 6-Video 1). Notably, the rates of increase in AF546-Fab’ MFI, calculated from the slopes of AF546-Fab’ MFI versus time plots in individual cells, were significantly higher during B-cell contraction than before B-cell contraction in control cells and conditions (Figure 6D-K). Significantly, inhibiting B-cell contraction by CK-666 treatment at 0 (Figure 6A, D, and H, and Figure 6-Video 1A and D) or 2 min (Figure 6A, E, and I), Wisko (Figure 6B, F, and J, and Figure 6-Video 1B and E), and cNKO (Figure 6C, G, and K, and Figure 6-Video 1C and F) abolished the increases in AF546-Fab’ accumulation rates. We further examined the peak FI of AF546-Fab’ in individual microclusters as a measure of the BCR molecular density in individual clusters. AF546-Fab’ clusters were identified based on their diameters ≥250 nm, peak FI ≥1.1 fold outside the B-cell contact zone, and trackable for ≥20 sec (Figure 6L and Figure 6-figure supplement 2). AF546-Fab’ microclusters could not be identified during the early stage of B-cell spreading. Time-lapse imaging by TIRF enabled us to measure the rate of increase in AF546-Fab’ peak FI in individual clusters (Figure 6M and Figure 6-figure supplement 2). Consistent with our observation of AF546-Fab’ MFI increase in the contact zone, the peak FI of individual clusters increased at a faster rate during contraction than after contraction (when the contact area no longer decreased) (Figure 6N). Furthermore, CK-666 (Figure 6O), Wisko (Figure 6P), and cNKO (Figure 6Q) all significantly reduced the rate of increase in AF546-Fab’ peak FI in individual clusters. These results show that B-cell contraction significantly increases the molecular density of BCRs in BCR clusters.

Increased BCR molecular density by B-cell contraction reduces BCR phosphorylation levels in individual microclusters

To examine how BCR molecular density influenced BCR signaling capability, we immunostained B-cells interacting with AF546-Fab’-PLB for 1, 3, 5, and 7 min, for phosphorylated CD79a (pCD79a, Y182) and performed IRM and TIRF imaging (Figure 7A and H). We analyzed equal numbers of AF546-Fab’ clusters selected randomly, in the contact zone of B-cells interacting with Fab’-PLB for 1, 3, 5, and 7 min, using a gradient threshold of their AF546-Fab’ MFI, 1.1 to 4.1 fold of the background, and with diameter ≥250 nm (Figure 6-figure supplement 2). We determined the MFI of pCD79a and AF546-Fab’ in individual clusters and plotted the MFI ratio of pCD79a relative to AF546-Fab’ (reflecting the relative level of BCR phosphorylation) versus the AF546-Fab’ peak FI (reflecting BCR molecular density) in individual clusters (Figure 7B and C). The dot plots show that when the AF546-Fab’ peak FI of individual clusters was relatively low, the MFI ratios of pCD79a to AF546-Fab’ increased with the AF546-Fab’ peak FI in individual clusters of flox control B-cells (Figure 7B). When the AF546-Fab’ peak FI reached a certain level, the MFI ratios of pCD79a to AF546-Fab’ decreased as the AF546-Fab’ peak FI in individual clusters further increased (Figure 7A and B). Inhibition of B-cell contraction by cNKO reduced the AF546-Fab’ peak FI in individual clusters, maintaining it within a relatively low range, where the MFI ratios of pCD79a to AF546-Fab’ increased with the AF546-Fab’ peak FI (Figure 7C and D). Additionally, the average pCD79a to Fab’ MFI ratios were much higher in cNKO B-cells than flox control B-cells, when comparing AF546-Fab’ clusters with the same range of peak FI (Figure 7B-D). During the contraction stage (5 and 7 min), flox control B-cells exhibited increased AF546-Fab’ MFI (Figure 7E) but decreased pCD79a MFI (Figure 7F) and the MFI ratios of pCD79a relative to AF54-Fab’ (Figure 7G) in individual clusters, compared to the spreading stage (1 and 3 min). In contrast, non-contracting cNKO B-cells only slightly increased AF546-Fab’ MFI (Figure 7E) but significantly increased pCD79a MFI (Figure 7F) and the pCD79a to AF546-Fab’ MFI ratios (Figure 7G) in individual clusters at the contraction stage compared to the spreading stage. Consequently, individual clusters in non-contracting cNKO B-cells had significantly lower AF546-Fab’ MFI but significantly higher pCD79a MFI and pCD79a to AF546-Fab’ FIRs than contracting flox control B-cells at 5 and 7 min but not at 1 and 3 min (Figure 7E-G). Similarly, inhibiting B-cell contraction by treatment with the Arp2/3 inhibitor CK-666 at 2 min post-stimulation reduced AF546-Fab’ MFI (Figure 7I) but increased pCD79a MFI (Figure 7J) and the MFI ratios of pCD79a relative to AF546-Fab’ (Figure 7K) in individual clusters. These data suggest that increases in BCR molecular density in BCR clusters during B-cell contraction inhibit BCR phosphorylation.

Increased molecular density in BCR clusters leads to reductions in BCR phosphorylation.

(A-G) Flox control and cNKO B-cells incubated with AF546-Fab’-PLB were fixed at 1, 3, 5, and 7 min, permeabilized, stained for phosphorylated CD79a (pCD79a, Tyr182), and imaged using TIRF and IRM. (A) Representative IRM and TIRF images of a flox control versus a cNKO B-cell at 7 min. Scale bars, 2 µm. (B-D) Ratios of pCD79a MFI relative to AF546-Fab’ MFI were plotted against AF546-Fab’ peak FI in individual AF546-Fab’ clusters in the contact zone of flox control (B), cNKO B-cells (C), or flox control and cNKO B-cells overlay (D). AF546-Fab’ clusters were identified as described in Figure 6 and Figure 6-figure supplement 2, from an equal number of cells at the 4 time points. Data points represent individual AF546-Fab’ clusters with an equal number of clusters from each time point. The black diamond symbols represent the average ratios of pCD79a MFI to Fab’ MFI in individual BCR-Fab’ clusters within the indicated Fab’ peak FI range. The brown square symbols represent the fraction of the AF546-Fab’ clusters out of the total, within the indicated Fab’ peak FI range. Data were generated from 3 independent experiments with ∼20 cells and ≥125 clusters per condition per experiment. * p <0.05, *** p<0.001, by non-parametric student’s t-test. (E-G) The MFI (±SEM) of AF546-Fab’ (E) and pCD79a (F) and the MFI ratio (±SEM) of pCD79a relative to AF546-Fab’ (G) in individual AF546-Fab’ clusters at indicated times were compared between flox control and cNKO B-cells and between different times. (H-K) WT B-cells treated with CK-689 or CK-666 after 2 min-incubation with AF546-Fab’-PLB. (H) Representative IRM and TIRF images of a CK-689-versus a CK-666-treated B-cell at 7 min. Scale bars, 2 µm. (I-K) The MFI (±SEM) of AF546-Fab’ (I) and pCD79a (J) and the MFI ratio (±SEM) of pCD79a relative to AF546-Fab’ (K) in individual AF546-Fab’ clusters were compared between CK-689- and CK-666-treated B-cells after 7 min stimulation. Data points represent individual clusters. Horizontal solid lines in the violin plots represent the mean, while the dotted lines represent the quartiles of the distribution. Data were generated from 3 independent experiments with ∼20 cells per condition per experiment. * p <0.05, *** p<0.001, by non-parametric student’s t-test. The p-values in D were corrected using the Benjamini-Hochberg/Yekutieli method for false discovery rate control.

Increased BCR molecular density by B-cell contraction promotes the disassociation of the stimulatory kinase Syk from BCR microclusters

Increased BCR molecular density may promote signaling attenuation by inducing the disassociation and/or dephosphorylation of stimulatory kinases from and at BCR clusters. To test this hypothesis, we analyzed the relative amounts of Syk, a major stimulatory kinase in the BCR signaling pathway, and its phosphorylated form pSyk (Y519/520) in individual BCR clusters in relation to the molecular density of BCRs. Splenic B-cells were incubated with Fab’-PLB for 3 and 7 min (when most cells were at the spreading and contraction phase, respectively), fixed, permeabilized, stained for Syk or pSyk, and imaged using TIRF. We measured MFI ratios of Syk relative to AF546-Fab’ in individual BCR clusters to reflect the relative amount of Syk associated with individual BCR clusters and analyzed their relationship with AF546-Fab’ peak FI (reflecting the molecular density within BCR clusters). AF546-Fab’ clusters were detected and analyzed as described above. In flox control B-cells, the highest fractions of BCR clusters had an AF546-Fab’ peak FI at the150∼200 range (Figure 8A, brown line and symbols). The average MFI ratios of Syk to Fab’ in individual clusters increased at a low peak FI range (<140) and did not significantly decrease until Fab’ peak FI reached a relatively high range (>280) (Figure 8A, black line and symbol). B-cells from cNKO mice exhibited a reduction in the Fab’ peak FI of clusters (Figure 8B and C, brown line and symbol) but an increase in the average Syk to Fab’ MFI ratios in clusters in a wide range of Fab’ peak FI, when compared to flox control B-cells (Figure 8B and C, black lines and symbols). However, the average Syk to Fab’ MFI ratios of cNKO B-cells decreased in clusters with Fab’ peak FI ≥220 and reduced to levels similar to those in flox control B-cells in clusters with Fab’ peak FI ≥240 (Figure 8B and C, black lines and symbols). These data suggest that increases in the molecular density of BCR clusters, reflected by Fab’ peak FI, induce disassociation of Syk from BCR clusters in both flox control and cNKO B-cells. Our results also show that BCR clusters in cNKO B-cells have significantly higher levels of Syk association than in flox control B-cells, even though they have similar Fab’ peak intensities.

Effects of BCR-Fab’ density on the association of Syk with BCR-Fab’ clusters and its phosphorylation.

Primary B-cells from flox control and cNKO mice were incubated with AF546-Fab’-PLB at 37°C, fixed at 3 or 7 min, stained for total Syk and phosphorylated Syk (pSyk Y519/520), and imaged by TIRF. (A-C) Ratios of Syk MFI relative to AF546-Fab’ MFI were plotted against AF546-Fab’ peak IF in individual AF546-Fab’ clusters in the contact zone of Flox control (A) and cNKO B-cells (B) and their overlay (C). AF546-Fab’ clusters were identified as described in Figure 6 and Figure 6-figure supplement 2 from an equal number of cells after 3- and 7-min stimulation. Data points represent individual AF546-Fab’ clusters with an equal number of clusters from each time point. The black diamond symbols represent the average ratios of Syk MFI to Fab’ MFI in individual AF546-Fab’ clusters with indicated Fab’ peak FI ranges. The brown square symbols represent the fraction of the AF546-Fab’ clusters out of the total at indicated Fab’ peak PI ranges. (D-F) Ratios of pSyk MFI relative to AF546-Fab’ MFI were plotted against AF546-Fab’ peak IF in individual AF546-Fab’ clusters in the contact zone of flox control (D) and cNKO B-cells (E) and their overlay (F). (G-I) MFI ratios of pSyk relative to AF546-Fab’ were plotted against AF546-Fab’ peak IF in individual pSyk puncta in the contact zone of Flox control (G) and cNKO B-cells (H) and their overlay (I). pSyk puncta were identified using the criteria: FI ≥1.3 fold of the background outside the B-cell contact zone and diameter ≥250 nm. The black diamond symbols represent the average ratios of pSyk MFI to Fab’ MFI in individual AF546-Fab’ clusters (D-F) or individual pSyk puncta (G-I) at indicated Fab’ peak FI ranges. The brown square symbols represent the fraction of the AF546-Fab’ clusters out of the total at indicated Fab’ peak PI ranges. Data points represent individual AF546-Fab’ clusters (D-F) or pSyk puncta (G and H), collected from an equal number of cells at 3 and 7 min. Data were generated from 3 independent experiments with ∼23 cells per condition per experiment. * p <0.05, ** p <0.01, *** p<0.001, by non-parametric student’s t-test, between AF546-Fab’ cluster group with different Fab’ peak FI ranges. The p-values in C, F and I were corrected using the Benjamini-Hochberg/Yekutieli method for false discovery rate control.

We next analyzed the relationship of the pSyk level in individual clusters with BCR molecular density using the method described above. We found that the MFI ratios of pSyk relative to AF546-Fab’ gradually decreased with increases in Fab’ peak FI in both flox control and cNKO B-cells (Figure 8D and E, black lines and symbols), even though we did not observe an increase in pSyk to Fab’ MFI ratio at the low Fab’ peak FI range. Similar to the Syk to Fab’ MFI ratio, the average pSyk to Fab’ MFI ratios of individual clusters in cNKO B-cells were much higher than those in flox control B-cells, except for those at the high Fab’ peak FI range (Figure 8D-F). To confirm this result, we analyzed equal numbers of pSyk clusters in the same cells, based on the criteria of ≥1.3 fold increase in the peak FI compared to the background outside the contact zone with a diameter of ≥250 nm. Similar to clusters identified by AF546-Fab’, the average MFI ratios of pSyk to Fab’ in these pSyk clusters decreased with increase in their Fab’ peak FI in both flox control and cNKO B-cells (Figure 8G-I, black lines and symbols). Again, the average pSyk to Fab’ MFI ratios of pSyk clusters were much higher in cNKO than flox control B-cells, but were reduced to similar levels in clusters with relatively high Fab’ peak FI (Figure 8I, black line and symbols). Similar reductions of total Syk and pSyk with increasing molecular density of BCR clusters suggest that the disassociation of Syk from BCR clusters, caused by cell contraction-induced increases in molecular density, contributes to BCR signaling attenuation.

Increased BCR molecular density by B-cell contraction promotes disassociation of the inhibitory phosphatase SHIP-1 from BCR microclusters

The inhibitory phosphatase SHIP-1 is essential for B-cell signaling attenuation (Brauweiler et al. 2000; Liu et al. 2011), suggesting that increases in the molecular density of BCR clusters by B-cell contraction may promote SHIP-1 recruitment. We used the methods described above to address this hypothesis, staining cells for total SHIP-1 and phosphorylated SHIP-1 (pSHIP-1 Y1020). We found that the average SHIP-1 to Fab’ MFI ratios in both flox control and cNKO B-cells decreased with Fab’ peak FI at similar rates (Figure 9A-C, black lines and symbols), even though inhibition of contraction by cNKO reduced the Fab’ peak FI of BCR clusters (Figure 9A-C, brown lines and symbols). Notably, the reduction in the SHIP-1 to Fab’ MFI ratios with increasing Fab’ peak FI occurred at the lowest detectable Fab’ peak PI (Figure 9A-C, brown lines and symbols), when the Syk to Fab’ MFI ratios increased and were sustained (Figure 8A-C). Furthermore, this reciprocal relationship between the SHIP-1 to Fab’ MFI ratio and Fab’ peak FI continued over the entire Fab’ peak FI range. It also remained the same in both flox control and cNKO B-cells (Figure 9A-C). These results suggest that SHIP-1 disassociates from BCR clusters as their molecular density increases, and that the SHIP-1 disassociation is more sensitive to the molecular density of BCR clusters than Syk disassociation.

The effects of BCR-Fab’ density on the association of SHIP-1 with BCR-Fab’ clusters and its phosphorylation.

Primary B-cells from flox control and cNKO mice were incubated with AF546-Fab’-PLB at 37°C, fixed at 3 or 7 min, stained for total SHIP-1 and phosphorylated SHIP-1 (pSHIP-1 Tyr1020), and imaged by TIRF. (A-C) Ratios of SHIP-1 MFI relative to AF546-Fab’ MFI were plotted against AF546-Fab’ peak IF in individual AF546-Fab’ clusters in the contact zone of Flox control (A) and cNKO B-cells (B). An overlay of flox control and cNKO plots is also shown (C). AF546-Fab’ clusters were identified as described in Figure 6 and Figure 6-figure supplement 2 from an equal number of cells after 3 and 7 min stimulation. Data points represent individual AF546-Fab’ clusters with an equal number of clusters from each time point. The black diamond symbols represent the average ratios of SHIP-1 MFI to Fab’ MFI in individual AF546-Fab’ clusters within indicated Fab’ peak FI ranges. The brown square symbols represent the fraction of the AF546-Fab’ clusters out of the total at indicated Fab’ peak FI ranges. (D-F) Ratios of pSHIP-1 MFI relative to AF546-Fab’ MFI were plotted against AF546-Fab’ peak IF in individual AF546-Fab’ clusters in the contact zone of flox control (D) and cNKO B-cells (E) and their overlay (F). (G-I) MFI ratios of pSHIP-1 relative to AF546-Fab’ were plotted against AF546-Fab’ peak IF in individual pSHIP-1 puncta in the contact zone of Flox control (G) and cNKO B-cells (H) and their overlay (I). The black diamond symbols represent the average ratios of pSHIP-1 MFI to Fab’ MFI in individual AF546-Fab’ clusters (D-F) or individual pSHIP-1 puncta (G-I) at indicated Fab’ peak FI ranges. The brown square symbols represent the fraction of the total clusters at indicated Fab’ peak FI ranges. pSHIP-1 puncta were identified using the criteria: FI ≥1.5 fold of the background outside the B-cell contact zone and diameter ≥250 nm. Data points represent individual AF546-Fab’ clusters (D-F) and pSHIP-1 puncta (G and H), collected from an equal number of cells at 3- and 7-min. Data were generated from 3 independent experiments with ∼23 cells per condition per experiment. * p <0.05, ** p <0.01, *** p<0.001, by non-parametric student’s t-test, between AF546-Fab’ cluster group with different Fab’ peak FI ranges. The p-values in C, F, and I were corrected using the Benjamini-Hochberg/Yekutieli method for false discovery rate control.

Similar to the relationship of total SHIP-1 with BCR molecular density, the average MFI ratios of pSHIP-1 relative to AF546-Fab’ in individual Fab’ clusters decreased with increases in Fab’ peak FI at similar rates in flox control and cNKO B-cells (Figure 9D-F, black lines and symbols), even though inhibition of contraction by cNKO reduced Fab’ peak FI of BCR clusters (Figure 9D-F, brown lines and symbols). The average pSHIP-1 to Fab’ MFI ratios in individual pSHIP-1 clusters, detected and analyzed in the same way as pSyk clusters, showed the same decrease with increases in their Fab’ peak FI in both flox control and cNKO B-cells (Figure 9G-I, black lines and symbols). Notably, the average pSHIP-1 to Fab’ MFI ratios in individual Fab’ or pSHIP-1 clusters in flox control and cNKO B-cells were at similar levels at the same Fab’ peak FI ranges (Figure 9F and I, black lines and symbols). These results indicate that contraction-induced molecular density increases within individual BCR clusters do not induce preferential recruitment of SHIP-1; instead, it promotes the disassociation of SHIP-1 from BCR clusters.

Discussion

When binding membrane-associated antigen, B-cells undergo actin-mediated spreading followed by a contraction, which amplifies BCR signaling and promotes immunological synapse formation (Fleire et al. 2006; Harwood and Batista 2011). We previously showed that B-cell contraction after spreading on antigen-presenting surfaces promotes BCR signaling attenuation (Liu et al. 2013a; Seeley-Fallen et al. 2022). However, how the actin cytoskeleton reorganizes as B-cells transition from spreading to contraction and how B-cell contraction downregulates BCR signaling have been elusive. Here we demonstrate that inner F-actin foci formed at the contact zone distal to the lamellipodial F-actin network promote B-cells to switch from spreading to contraction. These inner foci are derived from the lamellipodial F-actin network that mediates spreading, are generated by N-WASP-but not WASP-activated Arp2/3-mediated branched actin polymerization, and facilitate NMII recruitment, enabling B-cell contraction. B-cell contraction increases BCR molecular density in existing clusters, which promotes the disassociation of both the stimulatory kinase Syk and the inhibitory phosphatase SHIP-1, leading to signaling attenuation.

One significant finding of this study is that Arp2/3-mediated polymerization of branched actin is required for B-cell contraction. Arp2/3-mediated branched actin polymerization is known to drive B-cell spreading and to create actin centripetal flow at the contact zone between B-cells and antigen-presenting surface (Bolger-Munro et al. 2019). The actin structure that supports B- and T-cell spreading to form the immunological synapse with antigen-presenting cells is similar to lamellipodial F-actin networks found in adherent cells (Bunnell et al. 2001; Koestler et al. 2008; Bolger-Munro et al. 2019). Lamellipodial F-actin networks consist primarily of branched actin filaments polymerizing against the plasma membrane interspersed with bundled actin filaments (Krause and Gautreau 2014; Skau and Waterman 2015). Contractile actin structures, such as stress fibers, are typically generated from bundled actin filaments, as observed in adherent and migrating cells (Levayer and Lecuit 2012; Tojkander et al. 2015; Hammer et al. 2019). Here, we show that inner F-actin foci, generated by Arp2/3-mediated actin polymerization, transition B-cells from spreading to contraction. Furthermore, these inner F-actin foci are directly derived from lamellipodial F-actin networks. Based on the observed dynamics, we infer that instead of polymerizing against the plasma membrane, Arp2/3 appears to nucleate actin polymerization in the opposite direction, sustaining actin foci and their movement away from the lamellipodia. However, this study does not exclude the involvement of bundled actin filaments. Based on the requirement of formin-activated bundled actin filaments for lamellipodial F-actin networks and B-cell spreading (Wang et al. 2022), we can speculate that bundled actin filaments may play a role in the formation and movement of these inner F-actin foci, as well as in NMII recruitment.

Our work provides new insights into distinct functions of the actin nucleation-promoting factors WASP and N-WASP in controlling cell morphology and signaling. Immune cells, including B-cells, express both hematopoietic-specific WASP and the ubiquitous homolog of WASP, N-WASP. These two share high sequence homology, activation mechanism, and Arp2/3 activation function (Padrick and Rosen 2010). We previously identified distinct functions of these two factors that are unique to B-cells. While both are required for B-cell spreading, N-WASP plays a unique role in B-cell contraction. WASP and N-WASP double knockout B-cells fail to spread on antigen-presenting surfaces, but B-cell-specific N-WASP knockout enhances B-cell spreading and delays B-cell contraction (Liu et al. 2013a). Furthermore, these two factors reach peak activation at different times (phosphorylated WASP peaks during B-cell spreading, while phosphorylated N-WASP peaks during contraction) and are detected at distinct locations (the majority of WASP is at the periphery, and N-WASP is scattered across the B-cell contact zone) (Liu et al. 2013a). Here, we reveal the exact role of N-WASP in B-cell contraction – to generate inner F-actin foci from lamellipodial F-actin networks by activating Arp2/3-mediated actin polymerization. N-WASP- but not WASP-activated actin polymerization prolongs the relative lifetime of actin foci and mediates their inward motion toward the center of the contact zone. The delayed activation time and the location in the interior of the contact zone likely give N-WASP a unique opportunity to generate inner F-actin foci. As WASP and N-WASP suppress each other for activation in B-cells (Liu et al. 2013a), the timing and the location of their activation may depend on the relative levels of their expression and their abilities to compete for upstream and downstream molecules. As cNKO only delays and reduces but does not block B-cell contraction and inner F-actin foci formation, other actin factors may be involved, such as the WASP-family verprolin-homologous protein (WAVE) (Rotty et al. 2013).

Our recently published data show that NMII is required for B-cell contraction. Activated NMII is recruited to the B-cell contact zone in a SHIP-1-dependent manner and forms a peripheral ring surrounding the contact zone during B-cell contraction (Seeley-Fallen et al. 2022). Here, we further show that in addition to SHIP-1, N-WASP but not WASP is also involved in NMII recruitment and NMII ring-like structure formation, probably by generating inner F-actin foci. Collectively, these findings suggest that SHIP-1 coordinates with N-WASP to recruit NMII. Our previous finding that SHIP-1 promotes B-cell contraction by facilitating N-WASP activation (Liu et al. 2011; Liu et al. 2013a) supports this notion. However, it is surprising that the recruitment of NMII activated by BCR signaling to the contact zone is associated with inhibitory signaling molecules. BCR downstream signaling, including Ca2+ fluxes and Rho-family GTPase activation, likely activates NMII motor activity (Vicente-Manzanares et al. 2009). The activation switches NMII from the incompetent folded conformation to the competent extended conformation, enabling NMII molecules to bind to F-actin and assemble into contractible bipolar filaments and stacks (Matsumura 2005). A denser F-actin organization has been shown to increase NMII filament stacking (Fenix and Burnette 2018). Here, we showed that the inner F-actin foci generated by N-WASP-activated Arp2/3 are more stable and denser and thus likely promote NMII binding and stacking more efficiently than F-actin generated by WASP-activated Arp2/3. Indeed, our kymograph analysis revealed similar time windows and spatial locations for NMII accumulation and for generating inner F-actin foci from lamellipodial F-actin, supporting our hypothesis.

Wang et al. (Wang et al. 2022) recently showed that B-cells generate actomyosin arcs when interacting with membrane-associated antigen in the presence of adhesion molecules, as when interacting with professional antigen-presenting cells. In contrast to T-cells, B-cells can also respond to membrane-associated antigen without the help of adhesion molecules, when engaging antigen on pathogenic cells, like bacteria, parasites, and cancer cells. While the relationship between actomyosin arcs and inner F-actin foci remains to be explored, the role of inner F-actin foci in the formation of NMII ring-like structures revealed in our study suggests that the inner F-actin foci in the absence of adhesion molecules may be the facilitator or precursors of the actomyosin arcs. These structures can potentially be enhanced and matured by interactions between B-cells and antigen-presenting membranes mediated by adhesion molecules.

Our findings suggest an increase in the molecular density within BCR clusters or B-cell synapses as one of the mechanisms by which B-cell contraction promotes BCR signaling attenuation. During contraction, the molecular density of individual BCR clusters, measured by their MFI and peak FI of BCR clustered Fab’, increased faster than during the spreading and post-contraction phases. Surprisingly, increases in molecular density induced disassociation of both the stimulatory kinase Syk and the inhibitory phosphatase SHIP-1, contradicting the existing dogma of sequential association of stimulatory and inhibitory signaling molecules with the BCR (Franks and Cambier 2018). Interestingly, the disassociation of SHIP-1 is much more sensitive to BCR molecular density than Syk disassociation. Syk does not disassociate until the molecular density of BCR clusters reaches the top 10% range, while SHIP-1 disassociates from BCR clusters with increases over the entire detectable range of molecular densities. When B-cell contraction is inhibited, the molecular density of BCR clusters is reduced to a range with limited Syk disassociation and normal SHIP-1 disassociation, resulting in high Syk to SHIP-1 molecular ratios in BCR clusters than contracting B-cells, increasing BCR signaling levels. The resolution of our widefield TIRF imaging limits our ability to examine nascent BCR clusters that actively recruit signaling molecules. However, the consistency of the data from AF546-Fab’ and pSyk or pSHIP-1 clusters confirms our results. How the molecular density within BCR clusters promotes disassociation of signaling molecules is unknown. We speculate that molecular crowding may displace signaling molecules out of BCR clusters. Supporting this possibility, disassociation of the 145 kDa SHIP-1 is likely to be more sensitive to changes in the molecular density of BCR clusters, compared to disassociation of the 72 kDa Syk. However, these hypotheses need to be further examined.

An interesting finding of this study is that the pCD79a and pSyk levels were higher in individual BCR clusters of cNKO B-cells than those of flox control B-cells, even when BCR clusters had similar molecular densities. These data suggest additional mechanisms for B-cell contraction to promote BCR signaling attenuation. In addition to increasing molecular density within BCR clusters, the contractile forces generated by actomyosin rings on the B-cell membrane and BCR clusters may cause changes to the conformations of both BCRs and associated signaling molecules and their lateral interactions in the membrane. These changes may favor the disassociation rather than the association of signaling molecules with BCR clusters. Recently solved molecular assembly structures of both human and mouse BCRs (Dong et al. 2022; Su et al. 2022) support conformational and lateral molecular interaction changes as possible mechanisms for BCR signaling regulation. Actomyosin-mediated contractile forces were also shown to be required for BCR-mediated endocytosis of antigen (Natkanski et al. 2013; Hoogeboom et al. 2018; Maeda et al. 2021), which removes the BCR from the cell surface, downregulating the BCR surface signaling. Whether the inner F-actin foci identified here play any role in BCR endocytosis remains an interesting question. Our early finding that N-WASP is required for BCR endocytosis (Liu et al. 2013a) supports this notion. Similar to the differential impact of the molecular density on the disassociation of Syk and SHIP-1 from BCR clusters, B-cell contraction may differentially affect the interaction of surface BCRs with cytoplasmic and membrane-anchored signaling molecules, such as the lipidated and lipid raft-resident Src kinase Lyn that is responsible for phosphorylating both the immunoreceptor tyrosine-based activation motif (ITAM) of CD79a and the immunoreceptor tyrosine-based inhibitory motif (ITIM) that SHIP-1 binds to (Franks and Cambier 2018).

The results presented here have revealed novel insights into the mechanisms underlying actin-facilitated signaling attenuation of the BCR. Taking our previous and current data together, we propose a new working model for such actin-mediated signaling downregulation. Upon maximal spreading, N-WASP distal to lamellipodial networks activates Arp2/3-mediated branched actin polymerization, which sustains actin foci originating from lamellipodia and their movement away from the lamellipodia towards the center of the B-cell contact zone, generating inner F-actin foci. NMII is then preferentially recruited to these relatively stable inner foci, forming ring-like actomyosin structures, which enable B-cell contraction. B-cell contraction pushes the BCR microclusters formed during B-cell spreading to the center of the contact zone, increasing their molecular density. Increased molecular density promotes disassociation of signaling molecules from BCR clusters, probably due to crowding and conformational changes, leading to signal downregulation. Inhibitory signaling molecules likely activate the actin reorganization that drives B-cell contraction, as both the activation of N-WASP and the recruitment of NMII to the B-cell contact zone depend on SHIP-1 (Liu et al. 2013a; Seeley-Fallen et al. 2022). Thus, actin reorganization downstream of inhibitory phosphatases reinforces signaling attenuation by driving B-cell contraction.

Materials and Methods

Key Reagents Table

Mice and B-cell isolation

Wild-type (WT) C57BL/6 mice and WASP knockout (WKO) mice on the C57BL/6 background were purchased from Jackson Laboratories. C56BL/6 mice expressing LifeAct-GFP transgene (Riedl et al. 2010) were kindly provided by Dr. Roberto Weigert at National Cancer Institute, USA. C56BL/6 mice expressing the LifeAct-RFP transgene were kindly provided by Dr. Klaus Ley at La Jolla Institute for Allergy & Immunology. C57BL/6 mice expressing the GFP-non-muscle myosin IIA (NMIIA) transgene were kindly provided by Dr. Robert Adelstein at the National Heart, Lung, and Blood Institute, USA. WKO mice were bred with LifeAct-GFP mice to obtain LifeAct-GFP-expressing WKO mice. GFP-NMIIA mice were crossed with LifeAct-RFP mice to generate mice expressing both transgenes. N-WASPflox/flox on a 129Sv background (Cotta-de-Almeida et al. 2007) were kindly provided by Dr. Lisa Westerberg at Karolinska Institute, Sweden. B-cell-specific N-WASP knockout mice (cNKO, CD19Cre/+N-WASPflox/flox) and floxed littermate controls (N-WASPflox/flox) were obtained by breeding N-WASPflox/flox mice with CD19Cre/+ mice on a C57BL/6 background.

Primary B-cells were isolated from the spleens of 6 to 18 week-old male or female mice, using a previously published protocol (Sharma et al. 2009). Briefly, mononuclear cells were isolated by Ficoll density-gradient centrifugation (Millipore Sigma), and T-cells were eliminated by complement-mediated cytolysis with anti-mouse CD90.2 mAb (BD Biosciences) and guinea pig complement (Innovative Research Inc). Monocytes and dendritic cells were eliminated by panning at 37°C and 5% CO2. Isolated B-cells were kept on ice in DMEM (Lonza) supplemented with 0.6% BSA (Thermo Fisher Scientific). All work involving mice was approved by the Institutional Animal Care and Usage Committee of the University of Maryland.

Pseudo-antigen-coated planar lipid bilayers

Planar lipid bilayers (PLB) were prepared using a previously described method (Dustin et al. 2007; Liu et al. 2012a). Briefly, liposomes were generated from a mixture of 5 mM (total concentration) 1,2-dioleoyl-sn-glycero-3-phosphocholine and 1,2-dioleoyl-sn-glycero-3-phosphoethanolamine-cap-biotin (Avanti Polar Lipids) at a 100:1 molar ratio by sonication. Glass coverslips, cleaned overnight with Piranha solution (KMG chemicals), were attached to 8-well chambers (Lab-Tek) and incubated with liposomes (0.05 mM) in PBS for 20 min at room temperature and washed with PBS. The chambers were then incubated with 1 µg/ml streptavidin (Jackson ImmunoResearch Laboratories) for 10 min, washed with PBS, and then incubated with 10 µg/ml mono-biotinylated Fab’ fragment of goat anti-mouse Ig(G+M) (pseudo-antigen) (Fab’-PLB) for 10 min, followed by PBS wash. For transferrin-coated PLB (Tf-PLB), 16 16 µg/ml biotinylated holoTF was used. To visualize Fab’ clustering, a mixture of 0.5 µg/ml Alexa Fluor (AF) 546-labeled and 9.5 µg/ml unlabeled mono-biotinylated Fab’ fragment of goat anti-mouse Ig(G+M) was used. The lateral mobility of AF546-Fab’ on the PLB was tested using fluorescence recovery after photobleaching (FRAP) to ensure ≥85% AF546 fluorescence recovery within 1 min after photobleaching using a Zeiss LSM 710 equipped with a 60X oil-immersion objective.

Mono-biotinylated Fab’ fragments were generated as previously described (Liu et al. 2011). Briefly, the disulfide bond linking the two Fab fragments of F(ab’)2 goat anti-mouse Ig(G+M) was reduced using 2-mercaptoethylamine HCL (Thermo Fisher Scientific) and biotinylated by using maleimide-PEG2-biotin (Thermo Fisher Scientific). Mono-biotinylated Fab’ fragments of goat anti-mouse Ig(G+M) were labeled with AF546 using an Alexa Fluor 546 antibody labeling kit (Thermo Fisher Scientific). The molar ratio of AF546 to Fab’ in the AF546-labeled Fab’ was ∼2 determined by a Nanodrop spectrophotometer (Nanodrop Technologies).

Total internal fluorescence microscopy

To visualize molecules proximal to interacting sites between B-cells and Fab’- or Tf-PLB, we utilized total internal reflection fluorescence microscopy (TIRF) and interference reflection microscopy (IRM). Images were acquired using a Nikon TIRF system on an inverted microscope (Nikon TE2000-PFS, Nikon Instruments Inc.) equipped with a 60X, NA 1.49 Apochromat TIRF objective (Nikon), a Coolsnap HQ2 CCD camera (Roper Scientific), and two solid-state lasers of wavelength 491 and 561 nm. IRM, AF488, and AF546 images were acquired sequentially.

The plasma membrane area of B-cells contacting PLB was determined using IRM images and custom MATLAB codes. Whether a B-cell contracted or not was determined using the area versus time plots, wherein if a B-cell’s contact zone area reduced by ≥5% for at least 10 sec after reaching a maximum value, it was classified as contracting. To image intracellular molecules, B-cells were incubated with Fab’-PLBs for varying lengths of time in PBS at 37°C, fixed with 4% paraformaldehyde, permeabilized with 0.05% saponin, and stained for various molecules. For live-cell imaging, B-cells were pre-warmed to 37°C and imaged as soon as B-cells were dropped into coverslip chambers coated with Fab’-PLB containing PBS in a humidity chamber at 37°C, at 2 sec per frame, up to 7 min. All images from multiple independent experiments were analyzed using NIH ImageJ and custom MatLab codes. Acquired fluorescence intensity (FI) data were normalized to the one with the lowest FI.

Inhibitors

CK-666 (50 µM, Millipore Sigma) was used to perturb Arp2/3 activity (Nolen et al. 2009), and its non-functional derivative CK-689 (50 µM, Millipore Sigma) as a control. CK-666 or CK-689 was added at either 0 min, the start of incubation with Fab’-PLB, or at 2 min when most B-cells reached maximum spreading. Notably, B-cells take approximately 1 to 1.5 min to land on PLB. The time when B-cells were added to Fab’-PLB is referred to as 0 min, and the time when B-cells landed on PLB as the start of spreading. The effectiveness of CK-666 was determined by its inhibitory effects on the recruitment of Arp2/3, stained by an anti-Arp2 antibody (Abcam), to the B-cell contact zone using TIRF (Figure 1-figure supplement 2). Wiskostatin (Wisko, 10 µM, Millipore Sigma) was used to perturb N-WASP activity in B-cells (Peterson et al. 2004), with DMSO used as a vehicle control. Splenic B-cells were pretreated with Wisko for 10 min at 37°C before and during incubation with Fab’-PLB. The effectiveness of Wisko was determined by its inhibitory effects on the level of phosphorylated N-WASP in the B-cell contact zone using immunostaining and TIRF (Figure 1-figure supplement 4A and C). Possible effects of Wisko on WASP activation were evaluated by measuring the mean fluorescence intensity (MFI) of phosphorylated WASP in the contact zone of B-cells treated with or without Wisko for 10 min (Figure 1-figure supplement 4B and D).

Analysis of the actin cytoskeleton

F-actin was visualized by phalloidin staining in fixed cells and by LifeAct-GFP or LifeAct-RFP expressed by primary B-cells from transgenic mice in live cells. Inner F-actin foci, visualized by both phalloidin staining and LifeAct-GFP, were identified using NIH ImageJ based on the following three criteria: 1) ≥250 nm in diameter, 2) peak fluorescence intensity (FI) ≥2 fold higher than the FI of a nearby area containing no foci, and 3) ≥1 µm away from the outer edge of the B-cell contact zone. The horizontal or vertical length of a focus was measured, and the lesser of the two values was used as its diameter. To analyze the spatiotemporal relationship between inner F-actin foci and the lamellipodial F-actin network, we generated 8 radially and equally spaced kymographs from each cell using time-lapse images and MATLAB. Each kymograph was either classified as contracting or not contracting based on the movement of the leading edge of the B-cell contact zone. The percentage of 8 kymographs from each cell exhibiting inner F-actin foci that could be traced back to lamellipodial F-actin when the B-cell switched from spreading to contraction was determined.

The relative speeds and lifetimes of F-actin foci were determined using three randomly positioned kymographs from each B-cell and F-actin focuses emerging during a 60-sec window right after B-cell maximal spreading. Only those remaining visible in individual kymographs for at least 4 sec were analyzed. The time duration of each F-actin foci detected in a kymograph was used to determine the relative lifetime. The distances individual F-actin foci moved during their lifetimes were used to determine the relative speed. The term ‘relative’ has been used because the disappearance of an F-actin focus could be due to its movement away from the region used for the kymograph or vertically from the TIRF evanescent field of excitation.

To determine the rate of myosin recruitment, GFP-NMIIA MFI in the B-cell contact zone was plotted over time, and the slope for the initial segment of the MFI versus the time plot was determined using linear regression. The percentage of B-cells with the NMIIA ring was determined by visual inspection.

Analysis of BCR-Fab’ clusters

BCR clusters were identified by clustering of AF546-Fab’ on PLBs using custom code by MATLAB. We utilized the median FI of the Fab’-PLB within the same area outside but near the B-cell contact zone as the background. The median, but not mean FI value was used for background FI calculations to minimize fluctuations due to debris. To ensure that individual clusters with varying FI were detected as distinct objects, we used 16 graded thresholds from 1.1 to 4.1 fold of the background (0.2 fold apart) to acquire 16 sets of binary masks for each frame of time-lapse images from each cell. When clusters were detected by multiple thresholds at the same location, only the one identified by the highest threshold was retained. Objects that were smaller than 250 nm in diameter or could not be tracked for at least 20 sec were eliminated. This allowed us to detect the position of BCR-Fab’ clusters and track them over time until they merged with other clusters. The horizontal or vertical length of a focus was measured, and the lesser of the two values was used as its diameter. We chose the peak FI as a metric for the extent of Fab’ clustering by the BCR, because it does not rely on the area occupied by each cluster. The rate of peak FI increase was determined by linear regression of peak FI versus time curves for each cluster for a given window of time.

BCR signaling

Splenic B-cells were incubated with AF546-Fab’-PLB at 37°C and fixed at 1, 3, 5, 7, and 9 min. After fixation, cells were stained for phosphorylated CD79a (pCD79a, Y182) (Cell Signaling Technology), Syk (pSyk, Y519/520) (Cell Signaling Technology), SHIP-1 (pSHIP-1, Y1020) (Cell Signaling Technology), or total Syk or SHIP-1 proteins (Thermo Fisher Scientific). We identified BCR-Fab’ clusters as described. We determined the peak FI of AF546-Fab’ and the MFI of AF546-Fab’, pCD79a, pSyk, pSHIP-1, Syk, or SHIP-1 within each cluster. The ratio of pCD79a MFI to AF546-Fab’ MFI in the same cluster was used to estimate the relative phosphorylation level of BCRs in that cluster. This MFI ratio was plotted against AF546-Fab’ peak FI to analyze the relationship between BCR phosphorylation and BCR density of individual clusters. We calculated the MFI ratio of Syk to Fab’ or SHIP-1 to Fab’ in individual clusters to estimate the relative recruitment level of Syk or SHIP-1 to BCR clusters. We plotted these MFI ratios against Fab’ peak FI to determine the relationship between Syk and SHIP-1 recruitment levels and BCR density in individual clusters. We calculated the MFI ratio of pSyk to Fab’ or pSHIP-1 to Fab’ to estimate the amount of pSyk or pSHIP-1 relative to BCR in individual clusters. We plotted these MFI ratios against Fab’ peak FI to determine the relationship between Syk or SHIP-1 phosphorylation and BCR density in individual clusters. We identified pSyk or pSHIP-1 puncta using the criteria: ≥1.3 fold of the background staining outside the B-cell contact zone and ≥250 nm in diameter. We calculated the MFI ratio of pSyk to Fab’ or pSHIP-1 to Fab’ in individual puncta to estimate the amount of pSyk or pSHIP-1 relative to BCR in individual puncta. We plotted these MFI ratios against Fab’ peak FI to determine the relationship between Syk or SHIP-1 phosphorylation and BCR density in individual puncta.

Statistical analysis

Statistical analysis was performed using the Mann-Whitney U non-parametric test for unpaired groups having different sample sizes or the Student’s t-test for paired groups with the same sample size. To compare curves, Kolmogorov-Smirnov test was used. Statistical analyses were performed in Microsoft Excel, GraphPad Prism, and MATLAB. All data are presented as mean ± SEM (standard error of the mean). When testing multiple hypotheses, p--values acquired using t-tests were corrected using the Benjamini-Hochberg/Yekutieli method for false discovery rate control.

MATLAB scripts

All MATLAB scripts used for this study are available as supplemental materials.

Supporting information

eLife Assessment

The paper, which investigates mechanisms regulating the F-actin cytoskeleton in the B cell synapse, is an Important contribution to the study of B cell immunology and cell biology. The evidence provided for a key role of N-WASP regulation of F-actin proximal to the B cell receptor is solid, with parts of it being compelling.

Reviewer #1 (Public Review):

In this study, the authors demonstrated a new model that B cell contraction after antigen encountering was dependent on N-WASP-branched actin polymerization. This statement is achieved by a systemic comparison of genetic modified mice vs wild type mice or inhibitor treated cells vs control cells. By imaging how B cells interact with antigen-coated planar lipid bilayer, the authors further suggested that the contraction event may provide B cells a channel to dismiss downstream kinase for a purpose to attenuate B cell activation signaling. Even though this manuscript is well written and packaged, however there are a few points that should be carefully addressed and revised.

The first major issue is related to the imaging and tracking experiment to examine the formation and migration of F-actin foci as illustrated in figure 3. The formation and centripetally migration of F-actin foci is a significant finding of this MS for the promotion of B cells to switch from spreading to contraction response. Thus, I may suggest to recommend the authors to conduct one more rigorous fluorescent molecular tracking experiment to confirm this phenomenon. Molecular tracking usually requires low labeling density, and the lifeact-GFP labeling here do not meet this requirement which may cause misidentification of the moving molecules. Permeable dye-based fluorescent speckle microscopy is recommended here to track the actin foci if applicable (P. Risteski, Nat. Rev. Mol. Cell Biol., 2023, DOI: 10.1038/s41580-023-00588-w & K. Hu, et al, Science, 2007, 315, 111-115). Additionally, kymograph is used for foci tracking in figure3 and figure4. Kymograph is indeed a powerful tool for tracking cell protrusion and retraction but is fairly suitable here, since a F-actin focus is a concentrated point which may not move strictly along the selected eight lines generating kymograph. Other imaging processing method should be used to track the foci, for example, time series max projection is recommended if applicable.

The second major issue is about the relationship between actin foci formation and NMII recruitment in figure 5. The author concludes that 'N-WASP and Arp2/3 mediated branched actin polymerization promotes the recruitment and the reorganization of NMII ring-like structures by generating inner F-actin foci in the contact zone'. However, there is a lack of strong evidence to directly show the mechanism by which myosin is recruited and the up and down stream relationship between actin foci migration and myosin recruitment. Since myosin-induced actin retrograde flow is a classical model in adherent cells, is it possible that, here also in activated B cells, the recruited myosin driven the formation and migration of actin foci? This reviewer may recommend the author to investigate whether Myosin blocking (e.g., using Y27632) can eliminate the F-actin foci formation and migration.

Reviewer #2 (Public Review):

Bhanja et al have examined how actin polymerization switch B-cell receptor (BCR) signaling from amplification to attenuation. The authors have examined B cell spreading and contraction using lipid bilayers to assess the molecular regulation of BCR signalling during the contraction phase. Their data provide evidence for that N-WASP activated Arp2/3 generates centripetally moving actin foci and contractile actomyosin from lamellipodia actin networks. This generates BCR dense foci that pushes out both stimulatory kinases and inhibitory phosphatases. The study provides novel insight into how B cells upon activation attenuate BCR signalling by contraction of the actin cytoskeleton and clustering of BCR foci and this dynamic response is mediated by N-WASP and Arp2/3.

Strengths: The manuscript is well written and results, methods, figures and legends described in detail making it easy to follow the experimental setup, analysis, and conclusions. The authors achieved their aims, and the results support their conclusions.

Weaknesses: Minor as listed below. The working hypothesis of molecular crowding as a way to push out signalling molecules from the BCR dense foci is interesting. The authors provide evidence for that this is an active process mediated by N-WASP - Arp2/3 induced actin foci. Another possibility is that BCR dense foci formation is an indirect consequence of lamellipodia retraction. Future works should define the specific role of N-WASP, Arp2/3 and actin in the process to form BCR dense foci, especially as the BCR continue to signal in the cytoplasm.

Reviewer #3 (Public Review):

This work shows how, in the formation of the immune synapse, the B cell controls the contraction phase, the formation and retraction of actin structures concentrating the antigen (actin foci), and, ultimately, global signal attenuation. The authors use a combination of TIRF microscopy and original image quantification to show that Arp2/3 activated by N-WASP controls a pool of actin concentrated in foci (situated in the synapse), formed and transported centripetally towards the center of the synapse through myosin II mediated contractions. These contractions concentrate the B cell receptors (BCRs) in the center, promote disassembly of the stimulatory kinase Syk as well as the the disassociation from the BCR of the inhibitory phosphatase SHIP, process which entails the attenuation of the BCR signal.

The author prove their claims by mean of thorough image analysis, mainly observing and quantifying the fluorescence and the dynamics of single clusters of antigen and actin foci and analyzing two-colors dynamical images. They perform their observation in control cells, on pharmacologically perturbed cells where the action of Arp2/3 or N-WASP is inhibited, and on modified primary cells (primary derived from genetically engineered mice) to silence N-WASP or WASP. The work is sound and complete, the experiments technically excellent and well explained. Some experiments and discussions are objectively harder to describe, and given the length of the work, the reader might find itself lost some times. A graphical abstract/summary of the main way NWASP ultimately control signal attenuation would solve this minor point.

This work adds an important information to the current view of B cell activation, in particular it links the contraction phase to the actin foci that have been recently characterized. Moreover, the late phase of the immune synapse formation is, in general, poorly investigated, but it is crucial for the fate of the cell: this work provides an explanation for the attenuation of the signal that might lead to the termination of the synapse.

Author Response

The following is the authors’ response to the original reviews.

Reviewer #1 (Public Review):

The first major issue is related to the imaging and tracking experiment to examine the formation and migration of F-actin foci as illustrated in figure 3. The formation and centripetally migration of F-actin foci is a significant finding of this MS for the promotion of B cells to switch from spreading to contraction response. Thus, I may suggest to recommend the authors to conduct one more rigorous fluorescent molecular tracking experiment to confirm this phenomenon. Molecular tracking usually requires low labeling density, and the lifeact-GFP labeling here do not meet this requirement which may cause misidentification of the moving molecules. Permeable dye-based fluorescent speckle microscopy is recommended here to track the actin foci if applicable (P. Risteski, Nat. Rev. Mol. Cell Biol., 2023, DOI: 10.1038/s41580-023-00588w & K. Hu, et al, Science, 2007, 315, 111-115).

We thank the reviewer for the suggestion. We conducted the suggested experiment using membrane-permeable SiR-actin to track B-cell actin dynamics. Unfortunately, two significant issues prevented us from confirming the LifeAct-GFP results using fluorescent speckle microscopy. First, the concentration of SiR-actin required to visualize F-actin in the contact zone of mouse primary B-cells was relatively high due to their smaller sizes (~6 µm diameter) and non-adherent nature. With such a relatively high concentration of SiR-actin, we could not perform fluorescent speckle microscopy. Second, we observed that SiR-actin appeared to stabilize actin structures and reduce actin dynamics, further limiting its use in studying actin dynamics in B-cells.

Additionally, kymograph is used for foci tracking in figure3 and figure4. Kymograph is indeed a powerful tool for tracking cell protrusion and retraction but is not fairly suitable here, since a Factin focus is a concentrated point which may not move strictly along the selected eight lines generating kymograph. Other imaging processing method should be used to track the foci, for example, time series max projection is recommended if applicable.

We thank the reviewer for the suggestion and have tried the time series max projection. Unfortunately, it did not provide the resolution to identify individual actin foci, again probably due to the small size of primary mouse B-cells. While kymographs may not track the entire paths of these moving foci, we believe that the conclusions drawn from the kymography analysis in Figure 3 and 4 are reasonable. We generated eight kymographs for each cell in Figure 3 and three kymographs for each cell in Figure 4 to follow as many actin foci as possible within the spreading to contraction transition time window. Our analysis in Figure 3 identifies the fraction of actin foci originating from lamellipodia. In Figure 4, we used the kymographs to trace the path of putative clusters and used these to calculate their relative lifetimes and speed. While this is not what was suggested by the reviewer, our analysis provides qualitatively similar information to the time series max projection and reasonable comparisons between contracted and noncontracted cells, inhibitor-treated and untreated cells, and wild-type and WASP KO cells.

The second major issue is about the relationship between actin foci formation and NMII recruitment in figure 5. The author concludes that 'N-WASP and Arp2/3 mediated branched actin polymerization promotes the recruitment and the reorganization of NMII ring-like structures by generating inner F-actin foci in the contact zone'. However, there is a lack of strong evidence to directly show the mechanism by which myosin is recruited and the up and down stream relationship between actin foci migration and myosin recruitment. Since myosin-induced actin retrograde flow is a classical model in adherent cells, is it possible that, here also in activated B cells, the recruited myosin driven the formation and migration of actin foci? This reviewer may recommend the author to investigate whether Myosin blocking (e.g., using Y27632) can eliminate the F-actin foci formation and migration.

This is an excellent suggestion! In the revised manuscript, we have included new data showing that treatment with the non-muscle myosin II motor inhibitor blebbistatin, which is known to inhibit B-cell contraction but not spreading on Fab’-PLB (Seeley-Fallen et al. 2022. Frontiers in Immunology), interferes with the formation of inner actin foci ring-like structures, which are associated with B-cell contraction. These results together suggest that the generation of inner actin foci ring-like structure depends on the coordination between N-WASP-mediated actin polymerization and myosin contractile activity. We chose to use blebbistatin rather than Y27632 to inhibit non-muscle myosin II because in addition to the ROCK pathway, myosin light chain kinase can also activate myosin II, and Y27632 may have additional effects besides inhibiting myosin activity. The new data are shown in Figure 5G and H and discussed in the revised manuscript.

Reviewer #2 (Public Review):

Weaknesses: Minor as listed below. The working hypothesis of molecular crowding as a way to push out signalling molecules from the BCR dense foci is interesting. The authors provide evidence for that this is an active process mediated by N-WASP - Arp2/3 induced actin foci. Another possibility is that BCR dense foci formation is an indirect consequence of lamellipodia retraction. Future works should define the specific role of N-WASP, Arp2/3 and actin in the process to form BCR dense foci, especially as the BCR continue to signal in the cytoplasm.

We thank the reviewer for the comments. We have included the possibility that lamellipodial retraction may be involved in increasing the molecular density of BCR clusters and suggested future studies on the potential roles of N-WASP-dependent inner actin foci and actomyosin structures in BCR internalization and intracellular signaling in the Discussion section.

Reviewer #3 (Public Review):

The author prove their claims by mean of thorough image analysis, mainly observing and quantifying the fluorescence and the dynamics of single clusters of antigen and actin foci and analyzing two-colors dynamical images. They perform their observation in control cells, on pharmacologically perturbed cells where the action of Arp2/3 or N-WASP is inhibited, and on modified primary cells (primary derived from genetically engineered mice) to silence N-WASP or WASP. The work is sound and complete, the experiments technically excellent and well explained. Some experiments and discussions are objectively harder to describe, and given the length of the work, the reader might find itself lost some times. A graphical abstract/summary of the main way N-WASP ultimately control signal attenuation would solve this minor point.

We greatly appreciate the reviewer’s confirmation of our data quality and are delighted to accept the reviewer’s suggestion. In the revised manuscript, we have included a new figure (Figure 10) in the Discussion section, summarizing the results presented in the manuscript as a working model.

Reviewer #1 (Recommendations For The Authors):

Some minor points: Figure 1C, E, G and I shows three individual symbols, indicating three independent experiments described in legend. Please double check for accuracy.

It is better to show statistical data with representative repeat, not the merged means of independent experiments. For example, figure 1C even indicates three "0" data in CK-666 treated cells, meaning no contracting cell was found in ~75 cells, while there are other repeats showing 45% - 50% contracting cells. This applies to all figures involving individual cell imaging data, such as figure 2D, in which 30 cells from three independent experiments were pooled. The authors shall clearly state that those independent experiments are statistically indistinguishable before pooling the data.

We agree with the reviewer’s comments that these data have variability from individual mice, the quality of isolated primary B-cells, and the lateral mobility of planar lipid bilayers. To show the variability, we displayed the data from each experiment as individual data points. In the revised manuscript, we have utilized three colors of dots to represent three independent experiments in Figure 1C, E, G, and I, Figure 2B-G, and new Figure 5H, which show that the data from the three experiments have the same trend despite the variability.

In figure 7B-C, figure 8 and figure 9. The significant test results were hard to understand in which groups they compared. Please describe it in more detail in the figure legend or the method section.

In the legend, the authors claimed blue points in Figure 7B represented individual pCD79a clusters within an equal number of BCR clusters from each time points. The authors used means to qualify the change of blue points distribution. These shall be clearly stated in the Methods. Total BCR cluster numbers shall be shown also. This applies to Figure 7B, 7C, 7D and all figures in figure 8 and figure 9.

We thank the reviewer for pointing it out. We have revised Figures 7-9, where we utilized square braces to indicate groups of clusters (blue points) being compared. We have also provided additional information in the figure legend and Method sections.

Reviewer #2 (Recommendations For The Authors):

199-200: What is the consequence of increased WASP activation in N-WASP knockout B cells? Is this evaluated as increased pWASP activity and/or increased actin polymerization of WASP knockout B cells. Does WASP and N-WASP have an additive or counteractive effect on each other during spreading and contraction?

Indeed, the relationship between WASP and N-WASP, which are co-expressed in B-cells and other immune cells, is fascinating. Our previous studies, using WASP germline knockout, B-cellspecific N-WASP knockout, WASP and N-WASP double knockout mice, showed that WASP and N-WASP have both additive and counteractive effects during B-cell spreading, but B-cell contraction only depends on N-WASP (Liu et al. 2013. PLoS Biol). Double knockout B-cells fail to spread, and WASP knockout B-cells show reduced spreading but still contract, showing their additive effects. However, WASP and N-WASP suppress each other for activation, as detected by their phosphorylation. Phosphorylated WASP increases in the B-cell contact zone first, and phosphorylated N-WASP increases later when the phosphorylated WASP level decreases. Knocking out one of them enhances the phosphorylation of the other. Consequently, N-WASP knockout B-cells show increased spreading, probably due to enhanced activation of WASP, but exhibit delayed contraction. The revised manuscript has expanded the discussion on this area to relate it to the results presented in this manuscript.

560-563: Was Syk and SHIP-1 measured in the same cell? If not, the conclusion should be tempered.

Unfortunately, antibodies specific for Syk and SHIP-1 were from the same host, which did not allow us to stain them in the same cells. The revised manuscript has discussed this as a shortcoming of our work.

1204-1205: Explain better "three randomly positioned kymographs were generated" - how were they selected?

We apologize for this unclear sentence. The three kymographs were positioned to track as many inner F-actin foci as possible.

328: Change "abolished" to "reduced" to describe the data. 354-356: Unclear sentence, please edit. 1171: (H) should be (G). 1325: "PI" should be "FI".

We thank the reviewer for finding these typos and unclear sentences. We have made the corrections accordingly.

Methods: The description of the TIRF microscopy method is good. Regarding the image analysis, it is somehow difficult to have a good understanding of what was analyzed just by reading the text. Please show an example of the pipeline for the analysis from a raw image and the processing steps.

Figure 6-figure supplement 2 shows the image analysis process for tracking Fab’ clusters. We utilized the same approach for the image analysis of Figures 7-9.

Discussion: Add a paragraph to state the limitations of the study. How do the findings here translate into in vivo activation of B cells and how can this be addressed based on the data presented in this study.

We thank the reviewer for the suggestion. In several paragraphs of the revised Discussion section, we have brought up the limitations of the study and how these limitations affect the data interpretation. In addition, we have added Figure 10 and the associated text to present our working model, which explains how our findings reveal the cellular mechanism by which BCR surface signaling amplification transitions into attenuation, likely occurring in vivo.

Figure 2: Add an example of the image analysis for foci determination. From the images, it is not always clear what is a foci and what is not which makes the "number of foci" data difficult to evaluate.

We have added arrows to Figure 2A to indicate all identified inner F-actin foci in images.

Figure 3: add a kymograph for the WKO analysis.

In the revised Figure 4, we have provided a kymograph of a WKO B cell.

Figure 4M: the analysis of the "relative speed" of the "WT" samples is lower compared to the other control samples "DMSO" and "CK-689". The conclusion is that WKO have similar "relative speed" as "WT" cells, but in fact the "WT" cells may have responded poorly in this experiment. What is the author's experience and explanation?

We agree that the relative speeds of inner actin foci in the contact zone of WT and WKO B-cells are relatively low compared to DMSO and CK-689. Based on our experience, this parameter is very sensitive to the lateral mobility of planar lipid bilayers. We could only perform one pair of conditions using live cell images each time. The WT and WKO experiments were done at the end and might use relatively aged liposomes. However, it did not affect the number of inner actin foci formed and their relative lifetime, consistent with their similar relative speeds. Unfortunately, we lost the LifeAct-GFP-expressing WKO mouse colony and cannot redo this experiment using freshly made liposomes within a reasonable time.

Figure 7B-D: Add a more detailed legend for the black and brown lines in the dot plots.

We have expanded the legend for Figure 7B-D to provide additional details.

Figure 8-9: Show representative images for SYK, pSYK, SHIP-1 and pSHIP-1. Add a more detailed legend for the black and brown lines in the dot plots.

We have provided representative images for Syk, pSyk, SHIP-1, and pSHIP-1 in revised Figure 8 and 9.

Reviewer #3 (Recommendations For The Authors):

From the paper one understands that NMII is recruited by the actin foci and this recruitment pushes the foci towards the center of the synapse, in what resembles a positive feedback. Could the authors better elucidate this point? What happen at the peak of NMII recruitment? Could this be a mechanism used by the cell to end the contact and detach (which probably cannot be observed in this experimental setup)?

This is an excellent comment! We have recently shown that NMIIA recruitment peaks right before B-cell contraction occurs, and inhibition of NMII by inhibitors or B-cell conditional knockout blocks B-cell contraction and enhances signaling (Seeley-Fallen et al. 2022. Frontiers in Immunology). In the revised manuscript, we have included new data showing that treatment with the NMII motor inhibitor blebbistatin, which is known to inhibit B-cell contraction but not spreading on Fab’-PLB (Seeley-Fallen et al. 2022. Frontiers in Immunology), interferes with the formation of inner actin foci associated with B-cell contraction. These results together suggest that the generation of inner actin foci depends on the coordination between N-WASP-activated actin polymerization and myosin contractile activity, supporting the reviewer’s comment. The new data are shown in Figure 5G and H and discussed in the revised manuscript.

Whether the recruited NMII pulls B-cells away from antigen-presenting surfaces remains an interesting question. We have previously shown that high-affinity interaction of surface BCRs with membrane-anchored antigen can cause NMII-dependent B-cell membrane permeabilization, which triggers lysosome exocytosis and lysosomal enzyme-mediated antigen cleavage, allowing antigen internalization and presentation to T-cells (Maeda et al. 2021. eLife). Furthermore, NMII is required for B cells to internalize surface antigens (Natkanski et al. 2013. Science). These results support the possibility that actomyosin structures formed during B-cell contraction may further drive B-cells to internalize antigen. We have discussed this interesting point in the revised manuscript.

Some experiments/quantification are a bit more complex than others and a reader might find hard to follow them (in particular figs 7,8 and 9). The comprehension could be improved by providing a guide to read them. E.g. it is not clear what the population distribution represents (and it is not particularly affected by any manipulation. How were the group for test chosen? It seems they are based on intensity categories taken every 100 units: is it the case? even if arbitrary, this should be stated it in the legend.

We thank the reviewer for understanding the complexity of image analysis and pointing out the unclear points. Based on the reviewer’s comments, we have revised Figures 7-9 and the figure legend. We utilized square brackets to indicate groups of clusters (blue points) being compared. The comparison groups were chosen arbitrarily based on Fab’ peak fluorescence intensity every 90 units for Figure 7 and 8 and every 100 units for Figure 9.

Can the author speculate on how the actin organization passes from actin foci to recruitment of NMII and arc formation? Is it a rearrangement of the actin network (percolation) or simply recruitment of monomers?

Our previous and new results show that both N-WASP-activated Arp2/3 and NMII are required to form inner F-actin foci. Based on these results, we speculate that N-WASP and Arp2/3mediated actin polymerization may initiate the process and recruit NMII, and recruited NMII coordinates with actin polymerization to reorganize actin structures, promoting inner actin foci maturation and arc formation. We have included these possibilities in the revised discussion.

The role of SHIP recruitment as way to inhibit the signal downstream of the BCR is an interesting finding. Is this related to the termination of the synapse? Could we relate the time scales (accurately measured in this work) to contact times observed in vivo?

The reviewer raises an interesting question. In the discussion section, we have speculated that the actomyosin structures responsible for B-cell contraction are potentially the precursor cytoskeleton structures for antigen internalization. However, the relationship of B-cell contraction and signaling attenuation with the termination of the synapse remains unclear.

The BCR has been shown to be internalised mechanically: do these new data suggest a mechanisms for force generation in antigen internalization at the actin foci? Related to that, how do the dynamics of N-WASP recruitment relate to the force measurement highlighted in Traction Force Microscopy experiments (see for example Wang Sci.Signal. 2018, Kumari Nat.Comm.2019)? What happens in situation when the actin foci are unable to get transported, e.g. as on the more classical antigen on coverslip configuration?

Indeed, our results allow us to speculate that the actomyosin structures responsible for B-cell contraction potentially contribute to antigen internalization by mechanical forces. We previously showed that the B-cell-specific N-WASP knockout drastically reduced BCR internalization of soluble antigen (Liu et al. 2013. PLoS Biol), and that NMII is required for BCR internalization of membrane-associated antigen (Maeda et al. 2021. eLife and Natkanski et al. 2013. Science). The effect of N-WASP knockout on the internalization of membrane-associated antigen and traction forces generated at the contact membrane and whether traction forces are generated from the inner F-actin foci have not been determined but will be pursued in the future.

Our previous publication compared the BCR and actin dynamics of B-cells interacting with Fab’ tethered to planer lipid bilayers (Fab’-PLB) and cover glass (Fab’-G) (Ketchum et al. 2014. Biophys J). B-cells interacting with Fab’-G do not contract and generate inner F-actin foci and exhibit less dynamic BCR clusters and actin cytoskeleton than B-cells interacting with Fab’-PLB. Actin foci remain coincident with Fab’ clusters on glass rather than being positioned behind Fab’ clusters on PLB, thus driving their centripetal movement.

Minor remarks: When several experiments (mice) are presented in dot plots (e.g. fig 2D-G 4J-M), color dot plot (so called "smart plot") where each experiment is identified by a color, could be used to highlight the sample-to-sample variability.

This is an excellent suggestion. In the revised manuscript, we have utilized three shades of dots to represent the data points from three independent experiments.

Fig 6A: the fluorophore should be indicated in the picture (Fab'-AF546)

The suggested correction has been made.

Fig 6D: how is the contraction phase (purple rectangle) determined? Curve by curve or on the average curve? Please specify this in the legend.

The contraction phase (purple rectangle) was determined using the average curve of the contact area by IRM over time. We have added this sentence to the revised figure legend.

Minor typos in the material and methods: in some case C56BL/6 is written instead of C57BL/6 Corrected.

Version 2

Abstract

Abstract

Antigen-induced B-cell receptor (BCR) signaling is critical for initiating and regulating B-cell activation. The actin cytoskeleton plays essential roles in BCR signaling. Upon encountering cell-surface antigens, actin-driven B-cell spreading amplifies signaling, while B-cell contraction following spreading leads to signal attenuation. However, the mechanism by which actin dynamics switch BCR signaling from amplification to attenuation is unknown. Here, we show that Arp2/3-mediated branched actin polymerization is required for B-cell contraction. Contracting B-cells generate centripetally moving actin foci from lamellipodial F-actin networks in the B-cell plasma membrane region contacting antigen-presenting surfaces. Actin polymerization driven by N-WASP, but not WASP, initiates these actin foci and facilitates non-muscle myosin II recruitment to the contact zone, creating actomyosin ring-like structures. Furthermore, B-cell contraction increases BCR molecular density in individual clusters, leading to decreased BCR phosphorylation. Increased BCR molecular density reduced levels of the stimulatory kinase Syk, the inhibitory phosphatase SHIP-1, and their phosphorylated forms in individual BCR clusters. These results suggest that N-WASP-activated Arp2/3, coordinating with myosin, generates centripetally moving foci and contractile actomyosin ring-like structures from lamellipodial networks, enabling contraction. B-cell contraction attenuates BCR signaling by pushing out both stimulatory kinases and inhibitory phosphatases from BCR clusters, providing novel insights into actin-facilitated signal attenuation.

Introduction

B-cell-mediated antibody responses are essential for eliminating invading pathogens. B-cell receptors (BCRs) expressed on the B-cell surface detect the presence of cognate antigens. The binding of antigen to the BCR leads to the activation of signaling cascades (Reth and Wienands 1997; Dal Porto et al. 2004; Kwak et al. 2019), which induce transcriptional programs that prepare B-cells for proliferation and differentiation (Kurosaki et al. 2010; Shlomchik et al. 2019; Wang et al. 2020). BCR signaling also induces rapid antigen internalization, processing, and presentation for T-cell recognition, which provides the second signal required for B-cell clonal expansion and differentiation to high-affinity antibody-secreting cells and memory B-cells (Song et al. 1995; Gitlin et al. 2014). BCR signaling is tightly regulated by various external and internal factors to activate antibody responses that are specific and also qualitatively and quantitatively matched to the encountered antigen.

Antigen-induced receptor reorganization activates BCRs at the B-cell surface. Antigen binding leads to BCR clustering at lipid rafts, which enables raft-resident kinases, such as the Src kinases Lyn and Fyn, to phosphorylate immunoreceptor tyrosine-based activation motifs (ITAMs) in the cytoplasmic domains of the BCR signaling subunit CD79a/b heterodimer (Reth 1994; Pierce 2002; Sohn et al. 2008). Doubly phosphorylated ITAMs recruit and activate spleen tyrosine kinase (Syk), which in turn activates multiple downstream signaling pathways, including phospholipase Cγ2 (PLCγ2), Bruton’s tyrosine kinase (Btk), Ras-GTPase, and phosphatidylinositol-3 kinase (PI3K), initiating signaling cascades (Kurosaki 2000; Dal Porto et al. 2004; Tanaka and Baba 2020). Signaling activation also induces the recruitment and activation of inhibitory phosphatases, such as SH2-containing tyrosine phosphatase-1 (SHP-1) and phosphatidylinositol-5 phosphatase-1 (SHIP-1), to BCR signaling complexes (Brauweiler et al. 2000; Gross et al. 2009; Franks and Cambier 2018). SHIP-1 and SHP-1 negatively regulate BCR signaling by inactivating the plasma membrane docking lipids for stimulatory kinases, such as Btk and Akt (Aman et al. 1998; Bolland et al. 1998) and dephosphorylating BCR and its downstream signaling molecules (Mizuno et al. 2000; Adachi et al. 2001), respectively. The interplay between the stimulatory kinases and the inhibitory phosphatases controls the balance of antibody responses against pathogens and self. Deficiencies in stimulatory kinases by mutations, such as Btk, cause X-linked agammaglobulinemia (XLA) (Kinnon et al. 1993), while deficiencies in the inhibitory phosphatases SHP-1 or SHIP-1 result in autoimmune diseases (Pao et al. 2007; Leung et al. 2013). However, the mechanisms by which BCR signaling attenuation is initiated and regulated remain elusive.

B-cells encounter both soluble and membrane-associated antigens in vivo. Membrane-associated antigens include antigens on antigen-presenting cells, like follicular dendritic cells in B-cell follicles or germinal centers, and pathogenic cells, like bacteria, parasites, and cancer cells (Batista and Harwood 2009; Depoil et al. 2009; Gonzalez et al. 2009; Cyster 2010). The binding of multi-valent soluble antigen and membrane-associated antigen with any valency induces dynamic reorganization of surface BCRs into microclusters, triggering BCR signaling. Subsequently, surface BCRs continue moving to the plasma membrane region contacting antigen-presenting surfaces or to one B-cell pole in the case of soluble antigen, which leads to the growth and merger of BCR microclusters and the formation of immunological synapses (Carrasco et al. 2004; Harwood and Batista 2010) or supra-molecular activation complexes (Unanue and Karnovsky 1973; Schreiner and Unanue 1977; Tolar et al. 2009b; Harwood and Batista 2010).

Multiple mechanisms have been proposed for signaling initiation by antigen-induced surface BCR reorganization. The binding of surface BCRs to membrane-associated antigen has been shown to induce a conformational change in the BCR extracellular domain, exposing a proximal membrane region of membrane IgM that promotes receptor clustering (Tolar et al. 2009a; Shen et al. 2019). Antigen-binding also changes the conformation of the BCR cytoplasmic domains from a closed to an open form, facilitating the recruitment of signaling molecules (Tolar et al. 2005). Alternatively, antigen-BCR interaction can increase the molecular spacing of BCRs in clusters, facilitating BCR interaction with signaling molecules (Yang and Reth 2010; Kläsener et al. 2014). The inhibitory phosphatases SHP-1 and SHIP-1 are also recruited to BCR clusters (Adachi et al. 2001; Seeley-Fallen et al. 2014). However, the mechanisms underlying phosphatase recruitment and its relationship with BCR signaling activation complexes are unknown.

The actin cytoskeleton is essential for antigen-induced BCR reorganization on the B-cell surface in response to both soluble and membrane-associated antigen (Harwood and Batista 2011; Liu et al. 2013b; Song et al. 2013; Hoogeboom and Tolar 2016). Early signaling of the BCR triggers transient actin depolymerization via Rap GTPase and its downstream target cofilin (Freeman et al. 2011), which disassembles the existing cortical actin network that confines the lateral movement of surface BCRs (Treanor et al. 2010). Following this transient depolymerization, BCR signaling activates rapid actin polymerization through the actin nucleation promoting factors Wiskott-Aldrich Syndrome Protein (WASP) and neuronal-WASP (N-WASP), modulating BCR mobility and leading to F-actin accumulation at BCR-antigen interaction sites (Liu et al. 2013a; Rey-Suarez et al. 2020). Actin polymerization and treadmilling in B-cells stimulated by soluble antigen drive surface BCRs to cluster and move to one pole of the B-cell, forming a BCR cap (Schreiner and Unanue 1977; Liu et al. 2012a). Upon interacting with membrane-associated antigen, B-cells organize actin into two dynamic structures. One treadmills outwards, driving B-cell membrane spreading and expanding the B-cell membrane region contacting the antigen-presenting surface (contact zone), which enables more BCRs to engage antigen (Bolger-Munro et al. 2019). The other creates retrograde flow towards the center of the B-cell contact zone, driving the centripetal movement and growth of BCR microclusters (Liu et al. 2012b). Together, these processes amplify BCR signaling (Batista et al. 2010; Harwood and Batista 2011). The extent of B-cell spreading and the amount of BCR-antigen complexes gathered in the contact zone depend on BCR binding affinity and the density of antigen on the membrane (Fleire et al. 2006). Subsequent to spreading, B-cells contract, reducing the contact area, which drives BCR microclusters to merge into central clusters to form immunological synapses (Fleire et al. 2006; Liu et al. 2013a).

The actin cytoskeleton closely interplays with BCR signaling. We have previously shown that mouse primary B-cells with Btk deficiency (Liu et al. 2011) or double knockouts of the actin nucleation promoting factors WASP and N-WASP (Liu et al. 2013a) fail to spread on antigen-presenting surfaces and establish stable interactions with membrane-associated antigen, drastically reducing BCR signaling. Btk can activate WASP and N-WASP through Vav, the guanine nucleotide exchange factor of Cdc42 and Rac and phosphatidylinositol-5 kinase that generates phosphatidylinositol-4,5-biphosphate (PI4,5P2) (Sharma et al. 2009; Padrick and Rosen 2010). Surprisingly, B-cell-specific knockout of N-WASP (cNKO) but not WASP germline knockout (WKO) enhances B-cell spreading, delays B-cell contraction, and inhibits the centralization of BCR clusters at the contact zone (Liu et al. 2013a). Consistent with these findings, Bolger-Munro et al. have shown that knockdown of the actin nucleation factor Arp2/3 downstream of WASP and N-WASP disrupts the dynamic actin reorganization induced by membrane-associated antigen required for BCR microcluster growth and merger (Bolger-Munro et al. 2019). Using B-cell-specific and germline knockouts, we showed that in addition to N-WASP, the actin motor non-muscle myosin IIA (NMIIA) (Seeley-Fallen et al. 2022) and the actin-binding adaptor protein Abp1 (Seeley-Fallen et al. 2014) are required for B-cell contraction and BCR central cluster formation. Finally, Wang et al. recently showed that in the presence of the adhesion molecule ICAM on the antigen-presenting surface, B-cells form contractile actomyosin arcs, driving centripetal movement of BCR clusters in the B-cell contact zone (Wang et al. 2022). Together, these findings indicate a critical role of different actin networks in B-cell contraction and BCR signaling.

Our previous studies demonstrate that B-cell contraction is critical for BCR signaling attenuation. Delay or inhibition of B-cell contraction due to deficiencies in actin regulators, N-WASP, Abp1, or NMIIA, prolongs and/or increases BCR signaling by enhancing the activation of stimulatory kinases and suppressing the activation of inhibitory phosphatases, which elevates the production of autoantibody levels in mice (Liu et al. 2013a; Seeley-Fallen et al. 2014; Seeley-Fallen et al. 2022). N-WASP and NMIIA are not known to interact with kinases and phosphatases directly. The growth, merger, and centralization of antigen-BCR complexes at the B-cell contact zone during the B-cell contraction phase are associated with reduced BCR signaling capability (Liu et al. 2013a). These findings suggest that B-cell contraction is one of the mechanisms for inducing BCR signaling attenuation. However, how the actin cytoskeleton facilitates the transition of the spreading to contraction phase and how B-cell contraction switches BCR signaling from amplification to attenuation is unknown.

This study explores the mechanisms by which the actin cytoskeleton remodels from spreading lamellipodia to contractile structures and by which B-cell contraction suppresses BCR signaling. Our results show that the contractile actomyosin structures responsible for B-cell contraction originate from branched actin at spreading lamellipodia. N-WASP/Arp2/3-mediated actin polymerization prolongs the lifetime of the lamellipodial actin structures, enables NMIIA recruitment, and drives their movement to the center of the B-cell contact zone. B-cell contraction increases the molecular density within individual BCR-antigen clusters, which promotes the disassociation of both the stimulatory kinase Syk and the inhibitory phosphatases SHIP-1 from BCR clusters, leading to signal attenuation. Our study reveals a new mechanism underlying BCR signal downregulation.

Results

Arp2/3, activated by N-WASP but not WASP, is required for B-cell contraction

Arp2/3-generated branched F-actin is known to drive lamellipodial expansion for B-cell spreading (Bolger-Munro et al. 2019). However, whether branched F-actin is involved in the subsequent contraction phase is unknown. To address this, we perturbed the polymerization of branched F-actin using the Arp2/3 inhibitor CK-666 (50 µM) while using its inactive derivative CK-689 as a control. Pre-warmed splenic B-cells from WT C57BL/6 mice were incubated with monobiotinylated Fab’ fragment of anti-mouse IgM+G attached to planar lipid bilayers (Fab’-PLB) by biotin-streptavidin interaction and imaged live at 37°C using interference reflection microscopy (IRM). The contact area of B-cells treated with CK-689 rapidly increased upon contacting Fab’-PLB and reached a maximum at ≥0.5 min after the initial contact (Figure 1A, Figure 1-figure supplement 1, and Figure 1-Video 1A). Following maximal spreading, most B-cells reduced the area of their contact zone, indicating contraction (Figure 1A, Figure 1-figure supplement 1, and Figure 1-Video 1A). We classified a B-cell as contracting if its contact zone area reduced by ≥5% for at least 10 sec after reaching a maximum value. Based on the average timing for B-cell maximal spreading, we treated B-cells with CK-666 at the beginning of the incubation (Time 0), before B-cell spreading initiation, or at 2 min, when all B-cells had already spread. The effectiveness of CK-666 was detected by reduced Arp2/3 staining in the contact zone (Figure 1-figure supplement 2). As expected, CK-666 treatment at 0 but not 2 min reduced the kinetics of B-cell spreading (Figure 1-figure supplement 3). Importantly, CK-666 treatment at 0 and 2 min both significantly reduced the percentage of B-cells undergoing contraction (Figure 1A-C and Figure 1-Video 1A). The inhibitory effect of CK-666 on B-cell contraction, particularly CK-666 treatment after B-cell spreading, suggests that Arp2/3-mediated branched actin polymerization is required for B-cell contraction.

Arp2/3, activated by N-WASP but not WASP, is required for B-cell contraction.

Splenic B-cells were incubated with planar lipid bilayers coated with monobiotinylated Fab’ fragment of goat anti-mouse IgG+M (Fab’-PLB) in the absence and presence of various inhibitors and imaged live at 37°C by interference reflection microscopy (IRM). The B-cell plasma membrane area contacting Fab’-PLB (B-cell contact zone) was measured using IRM images and custom MATLAB scripts. (A) Representative IRM images of splenic B-cells from C57BL/6 mice treated with CK-689 or CK-666 (50 µM) before (0 min) and after maximal spreading (2 min). (B) Representative plots of the B-cell contact area versus time from one contracting cell and one non-contracting cell. (C) Percentages (±SEM) of B-cells that underwent contraction after treatment with CK-666 or CK-689. A B-cell was classified as contracting if its contact zone area was reduced by ≥5% for at least 10 sec after reaching a maximum value. (D) Representative IRM images of splenic B-cells from C57BL/6 mice treated with DMSO or Wiskostatin (Wisko, 10 µM) 10 min before and during incubation with Fab’-PLB. (E) Percentages (±SEM) of B-cells that underwent contraction after treatment with Wisko or DMSO. (F) Representative IRM images of splenic B-cells from flox control and B-cell-specific N-WASP knockout (cNKO) mice. (G) Percentages (±SEM) of cNKO or flox control B-cells that underwent contraction. (H) Representative IRM images of splenic B-cells from WT or WASP knockout mice (WKO). (I) Percentages (±SEM) of WKO or WT B-cells that underwent contraction. Data points in C, E, G, and I represent three independent experiments, ∼25 cells per condition per experiment, with each color representing one experiment. Scale bar, 2 µm. *p <0.05, ***p<0.001, by paired student’s t-test.

Figure supplement 1. B-cells spread and contract on Fab’-coated-planar lipid bilayers.

Figure supplement 2. CK-666 significantly decreases Arp2/3 recruitment to the B-cell contact zone.

Figure supplement 3. CK-666 treatment before but not after maximal B-cell spreading decreases the spreading kinetics.

Figure supplement 4. Wiskostatin treatment inhibits N-WASP activation while enhancing WASP activation in B-cells.

Figure 1–Video 1. Effects of CK-666, Wiskostatin, conditional N-WASP knockout, and WASP knockout on B-cell contraction.

WASP and N-WASP are actin nucleation-promoting factors upstream of Arp2/3 that are expressed in B-cells (Padrick and Rosen 2010). To determine if either or both were responsible for activating Arp2/3 for B-cell contraction, we utilized the N-WASP inhibitor wiskostatin (Wisko), and splenic B-cells from B-cell-specific N-WASP knockout mice (cNKO) and germline WASP knockout (WKO) mice (Westerberg et al. 2012; Liu et al. 2013a). Wisko has been shown to inhibit N-WASP activation while enhancing WASP activation in B-cells (Figure 1-figure supplement 4) (Liu et al. 2013a). We found that both Wisko (10 µM) (Figure 1D and E and Figure 1-Video 1B) and cNKO (Figure 1F and G and Figure 1-Video 1C), but not WKO (Figure 1H and I and Figure 1-Video 1D), significantly reduced the percentage of B-cells undergoing contraction, compared to the vehicle, flox, or WT controls. These results suggest that N-WASP-but not WASP-activated Arp2/3 mediates branched actin polymerization for B-cell contraction.

Arp2/3, downstream of N-WASP, generates inner F-actin foci, driving B-cell contraction

To understand how Arp2/3 drives B-cells to transition from spreading to contraction, we identified F-actin structures associated with contracting B-cells that were sensitive to CK-666 treatment. We visualized F-actin by phalloidin staining and compared F-actin organization in the contact zone of B-cells at the spreading (2 min) and contraction (4 min) phases using TIRF. While B-cells in both spreading and contraction phases exhibited phalloidin staining outlining the contact zone (Fig. 2A, green arrows), only B-cells in the contracting phase showed interior phalloidin patches brighter than the phalloidin staining at the periphery of the contact zone (Figure 2A, purple arrows). These F-actin patches were organized into a ring-like structure and resided ∼1 μm behind the spreading front, surrounding an F-actin-poor center (Figure 2A, purple arrows). Here, we refer these F-actin patches as inner F-actin foci. We identified inner F-actin foci based on whether their peak fluorescence intensity (FI) was ≥2 fold of the mean fluorescence intensity (MFI) of phalloidin in the no-foci area, had diameters of ≥250 nm, and were located 1 µm away from the edge of the contact zone. We found that such inner F-actin foci were detected in >60% of B-cells in the contracting phase (4 min) but only in <20% of B-cells in the spreading phase (2 min) (Figure 2B). CK-666 treatment at 0 min, which inhibited B-cell contraction, significantly reduced the percentage of B-cells showing inner F-actin foci at 4 min but not at 2 min (Figure 2B). CK-666 treatment did not affect the phalloidin staining outlining the contact zone (Figure 2A). Similarly, the percentage of cNKO B-cells showing inner F-actin foci was drastically reduced at 4 min but not at 2 min (Figure 2C). These results suggest that the formation of these inner F-actin foci is associated with B-cell contraction.

Arp2/3, downstream of N-WASP, generates inner F-actin foci, driving B-cell contraction.

(A-C) WT splenic B-cells were treated with CK-689 or CK-666 (50 µM) during incubation with Fab’-PLB (A and B), and flox control and cNKO B-cells were incubated with Fab’-PLB at 37°C (C). Cells were fixed at 2 and 4 min, permeabilized, stained for F-actin with phalloidin, and analyzed using TIRF. Shown are representative TIRF images of phalloidin staining in the contact zone of CK-689 and CK-666-treated B-cells (A, left panels) and fluorescence intensity (FI) profiles of phalloidin staining along a line crossing cells (A, right panels). Green arrows indicate lamellipodial F-actin, purple arrows indicate inner F-actin foci on the line, and blue arrows indicate all inner actin foci forming a ring-like structure. Percentages of cells (per image) (±SEM) with inner F-actin foci forming ring-like distribution among CK-689-versus CK-666-treated cells (B) and flox control versus cNKO B-cells (C) before (2 min) and after (4 min) contraction were determined by visual inspection of phalloidin FI line-profiles across the B-cell contact zones. Data points in B and C represent 3 independent experiments, with each color representing one experiment, 5 images per condition per experiment, and ∼15 cells per image. (D-G) Inner F-actin foci were identified by their diameter (≥250 nm), peak FI (≥2 fold of no foci area, and location (1 µm away from the outer edge) and quantified as the number per cell using TIRF images. (D) Shown are representative images of splenic B-cells from LifeAct-GFP-expressing mice treated with CK-689 or CK-666 from 0 min during incubation with Fab’-PLB at 37°C (top) and the average number (±SEM) of inner LifeAct-GFP foci per cell (bottom) at 2 min. (E) LifeAct-GFP B-cells were treated with CK-666 at 2 min. Shown are representative TIRF images of LifeAct-GFP in the contact zone of B-cells (top) and the average number (±SEM) of inner LifeAct-GFP foci (bottom) in the same cell 10s before and 20s after CK-666 treatment. Arrows indicate disappeared actin foci after CK666 treatment. (F) Shown are representative TIRF images of phalloidin-staining in the contact zone of flox control and cNKO B-cells after incubating with Fab’-PLB for 2 min (top) and the average number (±SEM) of inner F-actin foci per cell (bottom). (G) Shown are representative TIRF images of WT and WKO B-cells expressing LifeAct-GFP incubated with Fab’-PLB for 2 min and the average number (±SEM) of inner F-actin foci per cell (bottom). Data points represent individual cells from three independent experiments with 10 (D, F, and G) or 6 (E) cells per condition per experiment. Scale bar, 2 µm. ** p <0.01, *** p<0.001, by non-parametric student’s t-test.

Figure 2-Video 1. Effects of CK-666 and WKO on F-actin foci formation.

We further quantified the number of inner F-actin foci in individual B-cells from mice expressing the LifeAct-GFP transgene (Riedl et al. 2010) (Figure 2D, E, and G), which allowed us to monitor F-actin reorganization using live-cell imaging (Figure 2-Video 1), or using phalloidin staining in flox control and cNKO B-cells (Figure 2F). Consistent with the results with phalloidin staining, CK-666 treatment at time 0 significantly reduced the number of inner F-actin foci in the contact zone (Figure 2D and Figure 1-Video 1A and B). When we followed the same B-cells before and after CK-666 treatment at 2 min, many of the inner F-actin foci formed before the treatment (1 min 50 sec) disappeared after the treatment (2 min 20 sec), significantly reducing the number of inner F-actin foci (Figure 2E). Similar to the CK-666 treatment, cNKO cells significantly reduced the number of inner F-actin foci in the contact zone, compared to flox controls (Figure 2F). In contrast, WKO, which does not affect B-cell contraction, did not significantly change the number of inner F-actin foci, compared to WT control B-cells (Figure 2G and Figure 2-Video 1C and D). Thus, N-WASP-but not WASP-activated Arp2/3 drives the formation and the maintenance of contraction-associated inner F-actin foci.

Inner F-actin foci are derived from lamellipodial actin networks supporting the spreading membrane

We next examined the formation of contraction-associated inner F-actin foci utilizing live-cell TIRF imaging of B-cells from mice expressing LifeAct-GFP. We generated kymographs along eight lines from the center of each contact zone using time-lapse images of LifeAct-GFP (Figure 3A and B and Figure 3-figure supplement 1). Analysis of these kymographs showed that most F-actin foci were first detected closely behind lamellipodial F-actin networks. Following maximal spreading, these F-actin foci moved centripetally while increasing in intensity, becoming inner F-actin foci, in cells transitioning from spreading to contraction (Figure 3B, top panel, and Figure 3-figure supplement 1). However, such centripetally moving F-actin foci were not detected in B-cells that did not undergo contraction (Figure 3B, bottom panel). We quantified the percentage of the eight kymographs from each cell that exhibited lamellipodia-derived inner F-actin foci and found, on average, that six out of eight kymographs from contracting cells showed lamellipodia-derived inner F-actin foci, compared to only one or two kymographs from non-contracting cells (Figure 3C). To examine the temporal relationship between the generation of lamellipodia-derived inner F-actin foci and contraction, we plotted the percentage of kymographs with lamellipodia-derived inner F-actin foci over time with the spreading to contracting transition time set as 0 (Figure 3D). We found that the percentage of kymographs showing lamellipodia-derived inner F-actin foci peaked at almost the same time when the spreading transitioned to contraction (Figure 3D), suggesting a close temporal relationship between the two events.

Inner F-actin foci are originated from lamellipodia behind the spreading membrane.

Mouse splenic B-cells from LifeAct-GFP transgenic mice were treated with DMSO or Wisko (10 µM), imaged live using TIRF during incubation with Fab’-PLB at 37°C, and analyzed using kymographs generated by NIH ImageJ. (A) One frame of TIRF time-lapse images of LifeAct-GFP in the contact zone of B-cells treated with DMSO or Wisko and a WKO B-cell. Lines indicate eight kymographs that were randomly generated from each cell. (B) Representative kymographs were generated from TIRF time-lapse images of LifeAct-GFP at the red line in (A). Top panel, a contracting cell. Arrows indicate the start of contraction with inner F-actin foci originating from lamellipodia. Bottom panel, a non-contracting cell. Lamellipodia-derived inner F-actin foci were identified by their LifeAct-GFP FI ≥2 fold of their nearby region, migrating out of the lamellipodial F-actin toward the center of the contact zone, and trackable for >8 sec. (C) Percentages (±SEM) of kymographs showing inner F-actin foci originating from lamellipodia per cell that did and did not undergo contraction. Data were generated from 3 independent experiments with ∼10 cells per condition per experiment. (D) A histogram of inner F-actin foci emerging (expressed as percentages of the total events, blue line) over time relative to the time of B-cell contraction (defined as 0 sec, indicated by a purple dash line and arrow). Data were generated from 5 independent experiments with ∼9 cells per condition per experiment. (E) Percentage (±SEM) of inner F-actin foci originated from lamellipodia observed in 8 randomly positioned kymographs of each DMSO-or Wisko-treated WT or untreated WKO B-cell. Data were generated from 3 independent experiments with ∼10 cells per condition per experiment. Scale bars, 2 µm. *** p<0.001, by non-parametric student’s t-test.

Figure supplement 1. Emerging of Inner F-actin foci from lamellipodia.

Furthermore, the N-WASP inhibitor Wisko, but not WKO, significantly inhibited the formation of lamellipodia-derived inner F-actin foci (Figure 3E). Thus, inner F-actin foci originate from branched actin driven lamellipodia and form simultaneously with the transition of B-cell spreading to contraction.

N-WASP-activated Arp2/3 generates inner F-actin foci by sustaining the lifetime and the centripetal movement of lamellipodial F-actin

We examined the mechanism by which N-WASP and Arp2/3 generate inner F-actin foci by measuring their relative lifetime and mobility using kymographs generated from TIRF time-lapse images of B-cells expressing LifeAct-GFP. Inner F-actin foci were identified as described above, and their tracks were manually determined (Figure 4A, black dashed lines). The time window in which an inner F-actin patch could be detected in a kymograph was measured as the relative lifetime, as actin foci could move away from the kymograph line or the TIRF evanescent field (Figure 4A, right panels). The distance each F-actin focus moved during its lifetime was used to calculate its speed (Figure 4A, right panels). Compared to CK-689-treated B-cells, CK-666 treatment at time 0 significantly reduced the relative lifetime and the centripetal speed of inner F-actin foci (Figure 4B-D). After B-cells were treated with CK-666 at 2 min (the average time for B-cells to reach the maximal spreading), the relative lifetime and the centripetal speed of inner F-actin foci were significantly lower than before the treatment in the same cell (Figure 4E-G, line-linked dots). Similarly, the N-WASP inhibitor Wisko significantly reduced the relative lifetime and the centripetal speed of inner F-actin foci (Figure 4H-J); however, WKO had no significant effect (Figure 4K-M). These results show that N-WASP and Arp2/3 mediated branched actin polymerization prolongs the lifetime of lamellipodia-derived F-actin foci and drives them to move inward in the B-cell contact zone.

N-WASP-activated Arp2/3 sustains the lifetime and the centripetal movement of inner F-actin foci.

LifeAct-GFP-expressing B-cells were incubated with or without various inhibitors and imaged live by TIRF during interaction with Fab’-PLB at 37°C. Three kymographs were generated for each cell using time-lapse images and positioned to track as many inner actin foci as possible. (A) A representative kymograph from TIRF time-lapse images of a DMSO-treated B-cell (Left panels). Inner F-actin foci were identified as described in Figure 3, and those that emerged during the 60 sec window after maximal spreading (white rectangles in B) and can be tracked for ≥ 4 sec (dashed lines) in individual kymographs were analyzed. Relative lifetimes of inner F-actin foci were measured using the duration each focus could be detected in a kymograph. The relative distances traveled by the foci were measured using the displacement of each focus in a kymograph. Relative speed was calculated for each inner F-actin focus by dividing its relative distance by its relative lifetime (right panels). (B-D) B-cells were treated with CK-689 or CK-666 (50 µM) from the beginning of the incubation with Fab’-PLB (0 min). Shown are representative kymographs (B), relative lifetimes (C), and relative speed (D) of inner F-actin foci in CK-689-versus CK-666-treated B-cells. (E-G) B-cells were treated with CK-666 at maximal spreading (2 min). Shown are a representative kymograph of a CK-666-treated cell (E), relative lifetimes (F), and relative speeds (G) of inner F-actin foci in 30-sec windows before the inhibition and 10 sec after the inhibition in the same cells (linked by blue lines). (H-J) B-cells were treated with DMSO or Wisko (10 µM) 10 min before and during interaction with Fab’-PLB. Shown is a representative kymograph of a Wisko-treated B-cell (H), relative lifetime (I), and relative speed (J) of inner F-actin foci in DMSO versus Wisko-treated B-cells. (K-M) LifeAct-GFP-expressing WT and WKO B-cells were incubated with Fab’-PLB. Shown are a representative kymograph of a WKO B-cell (K), relative lifetime (L), and relative speed (M) of WT versus WKO B-cells. Data points represent the averaged values from inner F-actin foci in individual cells, with 3 kymographs per cell and ∼12 cells per condition per experiment from 3 independent experiments. Scale bar, 2 µm. * p <0.05, ** p <0.01, *** p<0.001, by non-parametric and paired student’s t-test.

N-WASP coordinates with NMII to generate inner actin foci and NMII ring-like structures

As non-muscle myosin II (NMII) is required for B-cell contraction (Seeley-Fallen et al. 2022), we examined the relationship between the formation of inner F-actin foci and the recruitment and reorganization of NMII in the contact zone using TIRF imaging of B-cells from mice expressing a GFP-NMIIA transgene. Upon interacting with Fab’-PLB, the GFP-NMIIA MFI in the contact zone of untreated WT B-cells increased rapidly in the first minute and slowly afterward (Figure 5A and B and Figure 5-Video 1). Wiskostatin treatment significantly reduced the GFP-NMIIA MFI in the contact zone (Figure 5B) and its initial rate of increase (as determined by the slope of the GFP-NMIIA MFI increase at 0∼30 sec time window) (Figure 5C). Kymographs generated from time-lapse TIRF images of B-cells from mice expressing GFP-NMIIA and LifeAct-RFP showed that recruited NMIIA accumulated between lamellipodia and inner F-actin foci when the foci moved centripetally away from lamellipodia (Figure 5D, white arrow, and Figure 5-Video 1). Recruited NMIIA reorganized with inner F-actin foci to form a ring-like structure in the contact zone (Figure 5A, D, and E, and Figure 5-Video 1). The percentage of B-cells with NMIIA ring-like structures, visualized by immunostaining, increased over time as more B-cells underwent contraction (Figure 5E and F). Compared to flox controls, the percentage of cNKO B-cells with NMIIA ring-like structures was significantly decreased (Figure 5E and F). Wiskostatin treatment also reduced NMIIA recruitment and ring-like structure formation (Figure 5-Video 1). Surprisingly, the percentage of WKO B-cells with NMIIA ring-like structure was higher than that of flox control B-cells (Figure 5E and F). Thus, N-WASP and Arp2/3 mediated branched actin polymerization promotes the recruitment and the reorganization of NMII ring-like structures.

N-WASP facilitates NMII recruitment and ring-like structure formation, and NMII promotes inner F-actin foci ring maturation.

(A-C) B-cells from mice expressing the GFP fusion of non-muscle myosin IIA (GFP-NMIIA) transgene were treated with DMSO or Wisko (10 µM) 10 min before and during incubation with Fab’-PLB. The B-cell contact zones were imaged live using TIRF. Shown are representative TIRF images of DMSO- and Wisko-treated B-cells at 30 sec (during spreading) and 2 min 30 sec (after maximal spreading) post landing (A, Scale bars, 2 µm), the averaged GFP-NMIIA MFI (±SEM) (B), and the initial rates of increasing (±SEM) of GFP-NMIIA in the contact zone (the slope of the initial GFP-NMIIA MFI versus time curves of individual cells) (C). Data points represent individual cells from 3 independent experiments with ∼6 cells per condition per experiment. * p <0.05, ***p<0.001, by Kolmogorov-Smirnov test (B) or non-parametric student’s t-test (C). (D) Primary B-cells from mice expressing both GFP-NMIIA and LifeAct-RFP transgenes were incubated with Fab’-PLB at 37°C and imaged live by TIRF. Shown are a representative TIRF image of a cell and a kymograph generated from time-lapse TIRF images at the yellow line. The purple arrow indicates the starting point of contraction, the white arrow GFP-NMIIA recruitment proximal to the spreading membrane, and the yellow arrow an F-actin (LifeAct-RFP) focus originating at the lamellipodia and moving away from the spreading membrane. (E, F) Primary B-cells from flox control, WKO, and cNKO mice were incubated with Fab’-PLB for indicated times. Cells were fixed, permeabilized, stained for NMII light chain, and imaged by IRM and TIRF. Shown are representative IRM and TIRF images (E) and percentages (±SD) of B-cells with the NMII ring-like structure in individual images (F), identified by visual inspection. The data were generated from 3 independent experiments with 5 images per condition per experiment. Scale bars, 2 µm. * p <0.05, ** p <0.01, *** p<0.001, by non-parametric student’s t-test. (G, H) WT splenic B-cells were treated with DMSO or Blebbistatin (Bleb, 50 µM) 20 min before and during incubation with Fab’-PLB at 37°C. Cells were fixed at 2 and 4 min, permeabilized, stained with phalloidin, and imaged by TIRF. Shown are representative TIRF images of the B-cell contact zone (G) and percentages of cells (±SEM) with inner F-actin foci forming ring-like distribution (H), determined as described in Figure 2. Data were generated from 3 independent experiments with ∼50 cells per condition per experiment with different color dots representing individual experiments. Scale bar, 2 µm. * p <0.05, ** p<0.01 by paired student’s t-test.

Figure 5-Video 1. Wiskostatin treatment inhibits NMII ring-like structure formation.

We next tested whether recruited NMII contributed to the formation of inner actin foci by inhibiting its motor activity using blebbistatin, which is known to impede B-cell contraction (Seeley-Fallen et al. 2022). Inner F-actin foci in the B-cell contact zone were identified by phalloidin staining, as described in Figure 2. Treatment with blebbistatin significantly reduced the percentages of WT splenic B cells exhibiting inner F-actin foci ring-like structures (Figure 5G and H). This result suggests that while NMII is recruited with the help of N-WASP and Arp2/3 mediated actin polymerization, its motor activity is critical for the maturation of F-actin structures associated with B-cell contraction.

B-cell contraction increases the BCR molecular density in individual clusters

To understand how B-cell contraction promotes BCR signaling attenuation, we examined the impact of B-cell contraction on the properties of BCR clusters. We first measured the MFI of AF546-Fab’ attached to PLB gathered by B-cells into the contact zone as an indication of the overall BCR molecular density. The clustering of AF546-Fab’ on PLB by B-cell binding reflects surface BCR clustering, as B-cell binding to transferrin (Tf)-tethered PLB does not cause surface BCRs to cluster and be phosphorylated (Figure 6-figure supplement 1) (Liu et al. 2011; Liu et al. 2013a). The MFI of AF546-Fab’ in the B-cell contact zone increased over time.

B-cell contraction increases the molecular density within BCR clusters.

Primary B-cells from WT mice were treated with CK-689 or CK-666 from the beginning of the incubation with AF546-Fab’-PLB (0 min) or at the maximal B-cell spreading (2 min) (A, D, E, H, I, N, O). WT B-cells were treated with DMSO or Wisko (10 µM) 10 min before and during the incubation with AF546-Fab’-PLB (B, F, J, P). B-cells from flox control and cNKO mice were incubated with AF546-Fab’-PLB (C, G, K, Q). The B-cell contact zones were imaged live by TIRF. (A-C) Representative time-lapse images at 30 sec (during B-cell spreading) and 2 min 30 sec (after maximal spreading) after cell landed. Scale bars, 2 µm. (D-G) The MFI of AF546-Fab’ in the contact zone was plotted over time. Purple rectangles indicate the contraction phase based on the changes in the average B-cell contact area over time. (H-K) Rates of AF546-Fab’ MFI increases in the B-cell contact zone before and during contraction were determined by the slope of AF546-Fab’ MFI versus time plots. Data points represent individual cells and were generated from 3 independent experiments with 6-12 cells per experiment. * p <0.05, ** p <0.01, *** p<0.001, by Kolmogorov-Smirnov test (D-G) or paired student’s t-test (H-K). (L) A representative frame from a time-lapse of a CK-689-treated B-cell (left) shows AF546-Fab’ clusters 30 sec after contraction began, and enlarged time-lapse images (right) show a single AF546-Fab’ cluster over a 40-sec time window after contraction began. AF546 clusters were identified using the criteria: ≥250 nm in diameter, ≥1.1 fold of FI outside the B-cell contact zone, and trackable for ≥ 20 sec. Scale bars, 2 µm. (M) The peak FI of an AF546-Fab’ cluster was measured over time, and the increasing rate of AF546-Fab’ peak FI of this cluster was determined by the slope of the plot. (N-Q) The rates (±SEM) of increase in AF546-Fab’ peak FI in individual clusters were compared between during and after contraction (N), between B-cells treated with CK-689 and CK-666 from 0 min (O), between DMSO- and Wisko-treated B-cells (P), and between flox control and cNKO B-cells (Q) after B-cells reached maximal spreading. Data points represent individual cells, the averaged slopes of clusters detected in one B-cell, from 3 independent experiments with 6∼12 cells per condition per experiment. *p <0.05, ** p <0.01, ***p<0.001, by non-parametric student’s t-test.

Figure supplement 1. Fab’-PLB, but not Tf-PLB, induces BCR clustering and phosphorylation.

Figure supplement 2. Tracking and analyzing AF546-Fab’ clusters in the B-cell contact zone.

Figure 6-Video 1. Inhibition of B-cell contraction reduces the molecular density within BCR clusters.

Treatment with CK-666, Wisko, or cNKO all reduced the AF546-Fab’ MFI, particularly during the time window of B-cell contraction in controls (Figure 6A-G, purple rectangles, and Figure 6-Video 1). Notably, the rates of increase in AF546-Fab’ MFI, calculated from the slopes of AF546-Fab’ MFI versus time plots in individual cells, were significantly higher during B-cell contraction than before B-cell contraction in control cells and conditions (Figure 6D-K).

Significantly, inhibiting B-cell contraction by CK-666 treatment at 0 (Figure 6A, D, and H, and Figure 6-Video 1A and D) or 2 min (Figure 6A, E, and I), Wisko (Figure 6B, F, and J, and Figure 6-Video 1B and E), and cNKO (Figure 6C, G, and K, and Figure 6-Video 1C and F) reduced the increases in AF546-Fab’ accumulation rates. We further examined the peak FI of AF546-Fab’ in individual microclusters as a measure of the BCR molecular density in individual clusters.

AF546-Fab’ clusters were identified based on their diameters ≥250 nm, peak FI ≥1.1 fold outside the B-cell contact zone, and trackable for ≥20 sec (Figure 6L and Figure 6-figure supplement 2). AF546-Fab’ microclusters could not be identified during the early stage of B-cell spreading. Time-lapse imaging by TIRF enabled us to measure the rate of increase in AF546-Fab’ peak FI in individual clusters (Figure 6M and Figure 6-figure supplement 2). Consistent with our observation of AF546-Fab’ MFI increase in the contact zone, the peak FI of individual clusters increased at a faster rate during contraction than after contraction (when the contact area no longer decreased) (Figure 6N). Furthermore, CK-666 (Figure 6O), Wisko (Figure 6P), and cNKO (Figure 6Q) all significantly reduced the rate of increase in AF546-Fab’ peak FI in individual clusters. These results show that B-cell contraction significantly increases the molecular density of BCRs in BCR clusters.

Increased BCR molecular density by B-cell contraction reduces BCR phosphorylation levels in individual microclusters

To examine how BCR molecular density influenced BCR signaling capability, we immunostained B-cells interacting with AF546-Fab’-PLB for 1, 3, 5, and 7 min, for phosphorylated CD79a (pCD79a, Y182) and performed IRM and TIRF imaging (Figure 7A and H). We analyzed equal numbers of AF546-Fab’ clusters selected randomly, in the contact zone of B-cells interacting with Fab’-PLB for 1, 3, 5, and 7 min, using a gradient threshold of their AF546-Fab’ MFI, 1.1 to 4.1 fold of the background, and with diameter ≥250 nm (Figure 6-figure supplement 2). We determined the MFI of pCD79a and AF546-Fab’ in individual clusters and plotted the MFI ratio of pCD79a relative to AF546-Fab’ (reflecting the relative level of BCR phosphorylation) versus the AF546-Fab’ peak FI (reflecting BCR molecular density) in individual clusters (Figure 7B and C). The dot plots show that individual AF546-Fab’ clusters with relatively low peak FI displayed increasing MFI ratios of pCD79a to AF546-Fab’ as the AF546-Fab’ peak FI rose in flox control B-cells (Figure 7B). Past a certain level of AF546-Fab’ peak FI, the MFI ratios of pCD79a to AF546-Fab’ decreased as the AF546-Fab’ peak FI in individual clusters further increased (Figure 7A and B). Inhibition of B-cell contraction by cNKO reduced the AF546-Fab’ peak FI in individual clusters, maintaining it within a relatively low range, where the MFI ratios of pCD79a to AF546-Fab’ increased with the AF546-Fab’ peak FI (Figure 7C and D). Additionally, the average pCD79a to Fab’ MFI ratios were much higher in cNKO B-cells than flox control B-cells, when comparing AF546-Fab’ clusters with the same range of peak FI (Figure 7B-D). During the contraction stage (5 and 7 min), flox control B-cells exhibited increased AF546-Fab’ MFI (Figure 7E) but decreased pCD79a MFI (Figure 7F) and the MFI ratios of pCD79a relative to AF54-Fab’ (Figure 7G) in individual clusters, compared to the spreading stage (1 and 3 min). In contrast, non-contracting cNKO B-cells only slightly increased AF546-Fab’ MFI (Figure 7E) but significantly increased pCD79a MFI (Figure 7F) and the pCD79a to AF546-Fab’ MFI ratios (Figure 7G) in individual clusters at the contraction stage compared to the spreading stage. Consequently, individual clusters in non-contracting cNKO B-cells had significantly lower AF546-Fab’ MFI but significantly higher pCD79a MFI and pCD79a to AF546-Fab’ FIRs than contracting flox control B-cells at 5 and 7 min but not at 1 and 3 min (Figure 7E-G). Similarly, inhibiting B-cell contraction by treatment with the Arp2/3 inhibitor CK-666 at 2 min post-stimulation reduced AF546-Fab’ MFI (Figure 7I) but increased pCD79a MFI (Figure 7J) and the MFI ratios of pCD79a relative to AF546-Fab’ (Figure 7K) in individual clusters. These data suggest that increases in BCR molecular density in BCR clusters during B-cell contraction inhibit BCR phosphorylation.

Increased molecular density in BCR clusters leads to reductions in BCR phosphorylation.

(A-G) Flox control and cNKO B-cells incubated with AF546-Fab’-PLB were fixed at 1, 3, 5, and 7 min, permeabilized, stained for phosphorylated CD79a (pCD79a, Tyr182), and imaged using TIRF and IRM. (A) Representative IRM and TIRF images of a flox control versus a cNKO B-cell at 7 min. Scale bars, 2 µm. (B-D) Ratios of pCD79a MFI relative to AF546-Fab’ MFI were plotted against AF546-Fab’ peak FI in individual AF546-Fab’ clusters in the contact zone of flox control (B), cNKO B-cells (C), or flox control and cNKO B-cells overlay (D). AF546-Fab’ clusters were identified as described in Figure 6 and Figure 6-figure supplement 2. Blue dots represent individual AF546-Fab’ clusters with an equal number of clusters from the 4 time points. The black line and diamond symbols represent the average ratios of pCD79a MFI to Fab’ MFI in individual BCR-Fab’ clusters within the indicated Fab’ peak FI range. The brown line and square symbols represent the fraction of the AF546-Fab’ clusters out of the total, within the indicated Fab’ peak FI range. Clusters were divided into three populations based on their peak AF546-Fab’ FI, relatively low (<190), medium (190-280), and high (>280, detected only in contracted cells), and the pCD79a to AF546-Fab’ MFI ratios of the three populations were compared (B and C). Data were generated from 3 independent experiments with ∼20 cells and ≥125 clusters per condition per experiment. * p <0.05, *** p<0.001, by non-parametric student’s t-test. The p-values in D were corrected using the Benjamini-Hochberg/Yekutieli method for false discovery rate control. (E-G) The MFI (±SEM) of AF546-Fab’ (E) and pCD79a (F) and the MFI ratio (±SEM) of pCD79a relative to AF546-Fab’ (G) in individual AF546-Fab’ clusters at indicated times were compared between flox control and cNKO B-cells and between different times. (H-K) WT B-cells treated with CK-689 or CK-666 after 2 min-incubation with AF546-Fab’-PLB. (H) Representative IRM and TIRF images of a CK-689-versus a CK-666-treated B-cell at 7 min. Scale bars, 2 µm. (I-K) The MFI (±SEM) of AF546-Fab’ (I) and pCD79a (J) and the MFI ratio (±SEM) of pCD79a relative to AF546-Fab’ (K) in individual AF546-Fab’ clusters were compared between CK-689- and CK-666-treated B-cells after 7 min stimulation. Data points represent individual clusters. Horizontal solid lines in the violin plots represent the mean, while the dotted lines represent the quartiles of the distribution. Data were generated from 3 independent experiments with ∼20 cells per condition per experiment. * p <0.05, *** p<0.001, by non-parametric student’s t-test.

Increased BCR molecular density by B-cell contraction promotes the disassociation of the stimulatory kinase Syk from BCR microclusters

Increased BCR molecular density may promote signaling attenuation by inducing the disassociation and/or dephosphorylation of stimulatory kinases from and at BCR clusters. To test this hypothesis, we analyzed the relative amounts of Syk, a major stimulatory kinase in the BCR signaling pathway, and its phosphorylated form pSyk (Y519/520) in individual BCR clusters in relation to the molecular density of BCRs. Splenic B-cells were incubated with Fab’-PLB for 3 and 7 min (when most cells were at the spreading and contraction phase, respectively), fixed, permeabilized, stained for Syk (Figure 8A) or pSyk (Figure 8E), and imaged using TIRF. We measured MFI ratios of Syk relative to AF546-Fab’ in individual BCR clusters to reflect the relative amount of Syk associated with individual BCR clusters and analyzed their relationship with AF546-Fab’ peak FI (reflecting the molecular density within BCR clusters).

Effects of BCR-Fab’ density on the association of Syk with BCR-Fab’ clusters and its phosphorylation.

Primary B-cells from flox control and cNKO mice were incubated with AF546-Fab’-PLB at 37°C, fixed at 3 or 7 min, stained for total Syk and phosphorylated Syk (pSyk Y519/520), and imaged by IRM and TIRF. (A) Representative IRM and TIRF images of Syk staining in a flox control versus a cNKO B-cell at 7 min (Scale bars, 2 µm). (B-D) Ratios of Syk MFI relative to AF546-Fab’ MFI were plotted against AF546-Fab’ peak IF in individual AF546-Fab’ clusters in the contact zone of Flox control (B) and cNKO B-cells (C) and their overlay (D). AF546-Fab’ clusters were identified as described in Figure 6 and Figure 6-figure supplement 2 from an equal number of cells after 3- and 7-min stimulation. Blue dots represent individual AF546-Fab’ clusters with an equal number of clusters from each time point. The black line and diamond symbols represent the average ratios of Syk MFI to Fab’ MFI in individual AF546-Fab’ clusters at indicated Fab’ peak FI ranges. The brown line and square symbols represent the fraction of the AF546-Fab’ clusters out of the total at indicated Fab’ peak FI ranges. (E) Representative IRM and TIRF images of pSyk staining in a flox control versus a cNKO B-cell at 7 min (Scale bars, 2 µm). (F-H) Ratios of pSyk MFI relative to AF546-Fab’ MFI were plotted against AF546-Fab’ peak IF in individual AF546-Fab’ clusters in the contact zone of flox control (F) and cNKO B-cells (G) and their overlay (H). Blue dots represent individual AF546-Fab’ clusters with an equal number of clusters from each time point. The black line and diamond symbols represent the average ratios of pSyk MFI to Fab’ MFI in individual AF546-Fab’ clusters at indicated Fab’ peak FI ranges. The brown line and square symbols represent the fraction of the AF546-Fab’ clusters out of the total at indicated Fab’ peak FI ranges. (I-K) MFI ratios of pSyk relative to AF546-Fab’ were plotted against AF546-Fab’ peak IF in individual pSyk puncta in the contact zone of Flox control (I) and cNKO B-cells (J) and their overlay (K). pSyk puncta were identified using the criteria: FI ≥1.3 fold of the background outside the B-cell contact zone and diameter ≥250 nm. Blue dots represent individual pSyk puncta with an equal number of clusters from each time point. The black line and diamond symbols represent the average ratios of pSyk MFI to Fab’ MFI in individual pSyk puncta at indicated Fab’ peak FI ranges. The brown line and square symbols represent the fraction of the pSyk puncta out of the total at indicated Fab’ peak FI ranges. Clusters were divided into three populations based on their peak AF546-Fab’ FI, relatively low (<190), medium (190-280), and high (>280, detected only in contracted cells), and the Syk (B and C) or pSyk (F, G, I, and J) to AF546-Fab’ MFI ratios of the three populations were compared. Data were generated from 3 independent experiments with ∼23 cells and ≥125 clusters per condition per experiment. * p <0.05, ** p <0.01, *** p<0.001, by non-parametric student’s t-test, between AF546-Fab’ cluster group with different Fab’ peak FI ranges. The p-values in D, H, and K were corrected using the Benjamini-Hochberg/Yekutieli method for false discovery rate control.

AF546-Fab’ clusters were detected and analyzed as described above. In flox control B-cells, the highest fractions of BCR clusters had an AF546-Fab’ peak FI at the150∼200 range (Figure 8A, top panels, and Figure 8B, brown line and symbols). The average MFI ratios of Syk to Fab’ in individual clusters increased at a low peak FI range (<140) and did not significantly decrease until Fab’ peak FI reached a relatively high range (>280) (Figure 8B, black line and symbol). B-cells from cNKO mice exhibited a reduction in the Fab’ peak FI of clusters (Figure 8A, bottom panels, and Figure 8C and D, brown line and symbol) but an increase in the average Syk to Fab’ MFI ratios in clusters in a wide range of Fab’ peak FI, when compared to flox control B-cells (Figure 8C and D, black lines and symbols). However, the average Syk to Fab’ MFI ratios of cNKO B-cells decreased in clusters with Fab’ peak FI ≥220 and reduced to levels similar to those in flox control B-cells in clusters with Fab’ peak FI ≥240 (Figure 8C and D, black lines and symbols). These data suggest that increases in the molecular density of BCR clusters, reflected by Fab’ peak FI, induce disassociation of Syk from BCR clusters in both flox control and cNKO B-cells. Our results also show that BCR clusters in cNKO B-cells have significantly higher levels of Syk association than in flox control B-cells, even though they have similar Fab’ peak intensities.

We next analyzed the relationship of the pSyk level in individual clusters with BCR molecular density using the method described above. We found that the MFI ratios of pSyk relative to AF546-Fab’ gradually decreased with increases in Fab’ peak FI in both flox control and cNKO B-cells (Figure 8E-G, black lines and symbols), even though we did not observe an increase in pSyk to Fab’ MFI ratio at the low Fab’ peak FI range. Similar to the Syk to Fab’ MFI ratio, the average pSyk to Fab’ MFI ratios of individual clusters in cNKO B-cells were much higher than those in flox control B-cells, except for those at the high Fab’ peak FI range (Figure 8E-H). To confirm this result, we analyzed equal numbers of pSyk clusters in the same cells, based on the criteria of ≥1.3 fold increase in the peak FI compared to the background outside the contact zone with a diameter of ≥250 nm. Similar to clusters identified by AF546-Fab’, the average MFI ratios of pSyk to Fab’ in these pSyk clusters decreased with increase in their Fab’ peak FI in both flox control and cNKO B-cells (Figure 8I-K, black lines and symbols). Again, the average pSyk to Fab’ MFI ratios of pSyk clusters were much higher in cNKO than flox control B-cells, but were reduced to similar levels in clusters with relatively high Fab’ peak FI (Figure 8K, black line and symbols). Similar reductions of total Syk and pSyk with increasing molecular density of BCR clusters suggest that the disassociation of Syk from BCR clusters, caused by cell contraction-induced increases in molecular density, contributes to BCR signaling attenuation.

Increased BCR molecular density by B-cell contraction promotes disassociation of the inhibitory phosphatase SHIP-1 from BCR microclusters

The inhibitory phosphatase SHIP-1 is essential for B-cell signaling attenuation (Brauweiler et al. 2000; Liu et al. 2011), suggesting that increases in the molecular density of BCR clusters by B-cell contraction may promote SHIP-1 recruitment. We used the methods described above to address this hypothesis, staining cells for total SHIP-1 (Figure 9A) and phosphorylated SHIP-1 (pSHIP-1 Y1020) (Figure 9E). We found that the average SHIP-1 to Fab’ MFI ratios in both flox control and cNKO B-cells decreased with Fab’ peak FI at similar rates (Figure 9A-D, black lines and symbols), even though inhibition of contraction by cNKO reduced the Fab’ peak FI of BCR clusters (Figure 9A-D, brown lines and symbols). Notably, the reduction in the SHIP-1 to Fab’ MFI ratios with increasing Fab’ peak FI occurred at the lowest detectable Fab’ peak FI (Figure 9B-D, brown lines and symbols), when the Syk to Fab’ MFI ratios increased and were sustained (Figure 8B-D). Furthermore, this reciprocal relationship between the SHIP-1 to Fab’ MFI ratio and Fab’ peak FI continued over the entire Fab’ peak FI range. It also remained the same in both flox control and cNKO B-cells (Figure 9B-D). These results suggest that SHIP-1 disassociates from BCR clusters as their molecular density increases, and that the SHIP-1 disassociation is more sensitive to the molecular density of BCR clusters than Syk disassociation.

The effects of BCR-Fab’ density on the association of SHIP-1 with BCR-Fab’ clusters and its phosphorylation.

Primary B-cells from flox control and cNKO mice were incubated with AF546-Fab’-PLB at 37°C, fixed at 3 or 7 min, stained for total SHIP-1 and phosphorylated SHIP-1 (pSHIP-1 Tyr1020), and imaged by TIRF. (A) Representative IRM and TIRF images of SHIP-1 staining in a flox control versus a cNKO B-cell at 7 min (Scale bars, 2 µm). (B-D) Ratios of SHIP-1 MFI relative to AF546-Fab’ MFI were plotted against AF546-Fab’ peak IF in individual AF546-Fab’ clusters in the contact zone of Flox control (B) and cNKO B-cells (C). An overlay of flox control and cNKO plots is also shown (D). AF546-Fab’ clusters were identified as described in Figure 6 and Figure 6-figure supplement 2 from an equal number of cells after 3 and 7 min stimulation. Blue dots represent individual AF546-Fab’ clusters with an equal number of clusters from each time point. The black line and diamond symbols represent the average ratios of SHIP-1 MFI to Fab’ MFI in individual AF546-Fab’ clusters at indicated Fab’ peak FI ranges. The brown line and square symbols represent the fraction of the AF546-Fab’ clusters out of the total at indicated Fab’ peak FI ranges. (E) Representative IRM and TIRF images of pSHIP-1 staining in a flox control versus a cNKO B-cell at 7 min (Scale bars, 2 µm). (F-H) Ratios of pSHIP-1 MFI relative to AF546-Fab’ MFI were plotted against AF546-Fab’ peak IF in individual AF546-Fab’ clusters in the contact zone of flox control (F) and cNKO B-cells (G) and their overlay (H). Blue dots represent individual AF546-Fab’ clusters with an equal number of clusters from each time point. The black line and diamond symbols represent the average ratios of pSHIP-1 MFI to Fab’ MFI in individual AF546-Fab’ clusters at indicated Fab’ peak FI ranges. The brown line and square symbols represent the fraction of the AF546-Fab’ clusters out of the total at indicated Fab’ peak FI ranges. (I-K) MFI ratios of pSHIP-1 relative to AF546-Fab’ were plotted against AF546-Fab’ peak IF in individual pSHIP-1 puncta in the contact zone of Flox control (I) and cNKO B-cells (J) and their overlay (K). pSHIP-1 puncta were identified using the criteria: FI ≥1.5 fold of the background outside the B-cell contact zone and diameter ≥250 nm. Blue dots represent individual pSHIP-1 puncta with an equal number of clusters from each time point. The black line and diamond symbols represent the average ratios of pSHIP-1 MFI to Fab’ MFI in individual pSHIP-1 puncta at indicated Fab’ peak FI ranges. The brown line and square symbols represent the fraction of the total pSHIP-1 puncta at indicated Fab’ peak FI ranges. Clusters were divided into three populations based on their peak AF546-Fab’ FI, relatively low (<200), medium (200-300), and high (>300, detected only in contracted cells), and the SHIP-1 (B and C) or pSHIP-1 (F, G, I, and J) to AF546-Fab’ MFI ratios of the three populations were compared. Data were generated from 3 independent experiments with ∼23 cells and ≥125 clusters per condition per experiment. * p <0.05, ** p <0.01, *** p<0.001, by non-parametric student’s t-test, between AF546-Fab’ cluster group with different Fab’ peak FI ranges. The p-values in D, H, and K were corrected using the Benjamini-Hochberg/Yekutieli method for false discovery rate control.

Similar to the relationship of total SHIP-1 with BCR molecular density, the average MFI ratios of pSHIP-1 relative to AF546-Fab’ in individual Fab’ clusters decreased with increases in Fab’ peak FI at similar rates in flox control and cNKO B-cells (Figure 9E-H, black lines and symbols), even though inhibition of contraction by cNKO reduced Fab’ peak FI of BCR clusters (Figure 9E-H, brown lines and symbols). The average pSHIP-1 to Fab’ MFI ratios in individual pSHIP-1 clusters, detected and analyzed in the same way as pSyk clusters, showed the same decrease with increases in their Fab’ peak FI in both flox control and cNKO B-cells (Figure 9I-K, black lines and symbols). Notably, the average pSHIP-1 to Fab’ MFI ratios in individual Fab’ or pSHIP-1 clusters in flox control and cNKO B-cells were at similar levels at the same Fab’ peak FI ranges (Figure 9H and K, black lines and symbols). These results indicate that contraction-induced molecular density increases within individual BCR clusters do not induce preferential recruitment of SHIP-1; instead, it promotes the disassociation of SHIP-1 from BCR clusters.

Discussion

When binding membrane-associated antigen, naive follicular B-cells undergo actin-mediated spreading followed by a contraction, which amplifies BCR signaling and promotes immunological synapse formation (Fleire et al. 2006; Harwood and Batista 2011). We previously showed that B-cell contraction after spreading on antigen-presenting surfaces promotes BCR signaling attenuation (Liu et al. 2013a; Seeley-Fallen et al. 2022). However, how the actin cytoskeleton reorganizes as B-cells transition from spreading to contraction and how B-cell contraction downregulates BCR signaling have been elusive. Here, we demonstrate that inner F-actin foci formed at the contact zone distal to the lamellipodial F-actin network promote B-cells to switch from spreading to contraction. These inner foci are derived from the lamellipodial F-actin network that mediates spreading, are generated by N-WASP-but not WASP-activated Arp2/3-mediated branched actin polymerization, and facilitate NMII recruitment. N-WASP-activated actin polymerization coordinates with NMII to form actomyosin ring-like structures, enabling B-cell contraction. B-cell contraction increases BCR molecular density in existing clusters, which promotes the disassociation of both the stimulatory kinase Syk and the inhibitory phosphatase SHIP-1, leading to signaling attenuation.

One significant finding of this study is that Arp2/3-mediated polymerization of branched actin is required for B-cell contraction. Arp2/3-mediated branched actin polymerization is known to drive B-cell spreading and to create actin centripetal flow at the contact zone between B-cells and antigen-presenting surface (Bolger-Munro et al. 2019). The actin structure that supports B- and T-cell spreading to form the immunological synapse with antigen-presenting cells is similar to lamellipodial F-actin networks found in adherent cells (Bunnell et al. 2001; Koestler et al. 2008; Bolger-Munro et al. 2019). Lamellipodial F-actin networks consist primarily of branched actin filaments polymerizing against the plasma membrane interspersed with bundled actin filaments (Krause and Gautreau 2014; Skau and Waterman 2015). Contractile actin structures, such as stress fibers, are typically generated from bundled actin filaments, as observed in adherent and migrating cells (Levayer and Lecuit 2012; Tojkander et al. 2015; Hammer et al. 2019). Here, we show that inner F-actin foci, generated by Arp2/3-mediated actin polymerization, transition B-cells from spreading to contraction. Furthermore, these inner F-actin foci are directly derived from lamellipodial F-actin networks. Based on the observed dynamics, we infer that instead of polymerizing against the plasma membrane, Arp2/3 appears to nucleate actin polymerization in the opposite direction, sustaining actin foci and their movement away from the lamellipodia. The natural retraction of lamellipodia may contribute to B-cell contraction, but the requirement of inner actin foci argues against it as a primary mechanism for B-cell contraction. This study does not exclude the involvement of bundled actin filaments. Based on the requirement of formin-activated bundled actin filaments for lamellipodial F-actin networks and B-cell spreading (Wang et al. 2022), we can speculate that bundled actin filaments may play a role in the formation and movement of these inner F-actin foci, as well as in NMII recruitment.

Our work provides new insights into distinct functions of the actin nucleation-promoting factors WASP and N-WASP in controlling cell morphology and signaling. Immune cells, including B-cells, express both hematopoietic-specific WASP and the ubiquitous homolog of WASP, N-WASP. These two share high sequence homology, activation mechanism, and Arp2/3 activation function (Padrick and Rosen 2010). We previously identified distinct functions of these two factors unique to B-cells. While both are required for B-cell spreading, N-WASP plays a unique role in B-cell contraction. WASP and N-WASP double knockout B-cells fail to spread on antigen-presenting surfaces, but B-cell-specific N-WASP knockout enhances B-cell spreading and delays B-cell contraction (Liu et al. 2013a). WASP and N-WASP appear to have a competitive relationship in B-cells, suppressing each other’s activation (Liu et al. 2013a). WASP is activated first during B-cell spreading and primarily localized at the periphery of the B-cell contact zone. N-WASP is activated later during B-cell contraction and scattered across the B-cell contact zone (Liu et al. 2013a). Here, we reveal the exact role of N-WASP in B-cell contraction – to generate inner F-actin foci from lamellipodial F-actin networks by activating Arp2/3-mediated actin polymerization. N-WASP-but not WASP-activated actin polymerization prolongs the relative lifetime of F-actin foci and facilitates their inward motion toward the center of the contact zone. The delayed activation time and the location in the interior of the contact zone likely give N-WASP a unique opportunity to generate inner F-actin foci. As cNKO only delays and reduces but does not block B-cell contraction and inner F-actin foci formation, other actin factors may be involved, such as the WASP-family verprolin-homologous protein (WAVE) (Rotty et al. 2013).

Our recently published data show that NMII is required for B-cell contraction (Seeley-Fallen et al. 2022). Activated NMII is recruited to the B-cell contact zone in a SHIP-1-dependent manner. NMII levels reach a plateau at the beginning of B-cell contraction, and NMII forms a peripheral ring surrounding the contact zone during B-cell contraction. Here, we further show that in addition to SHIP-1, N-WASP but not WASP is also involved in NMII recruitment and NMII ring-like structure formation, probably by initiating the generation of inner F-actin foci. Collectively, these findings suggest that SHIP-1 coordinates with N-WASP to recruit NMII. Our previous finding that SHIP-1 promotes B-cell contraction by facilitating N-WASP activation (Liu et al. 2011; Liu et al. 2013a) supports this notion. However, it is surprising that the recruitment of NMII activated by BCR signaling to the contact zone is associated with inhibitory signaling molecules. BCR downstream signaling, including Ca2+ fluxes and Rho-family GTPase activation, likely activates NMII motor activity (Vicente-Manzanares et al. 2009). The activation switches NMII from the incompetent folded conformation to the competent extended conformation, enabling NMII molecules to bind to F-actin and assemble into contractible bipolar filaments and stacks (Matsumura 2005). A denser F-actin organization has been shown to increase NMII filament stacking (Fenix and Burnette 2018). Here, we showed that the inner F-actin foci generated by N-WASP-activated Arp2/3 are more stable and denser and thus likely promote NMII binding and stacking more efficiently than F-actin generated by WASP-activated Arp2/3. Indeed, our kymograph analysis revealed similar time windows and spatial locations for NMII accumulation and for generating inner F-actin foci from lamellipodial F-actin, supporting our hypothesis. While NMII recruitment is facilitated by inner F-actin foci, the motor activity of NMII is required for the formation of the ring-like structures of inner F-actin foci in return, likely by driving their centripetal movement, thereby providing mechanical feedback for actin reorganization. However, the structural organization of inner F-actin foci and recruited NMII and their coordinated dynamics require further analysis with higher-resolution microscopy techniques.

Wang et al. (Wang et al. 2022) recently showed that B-cells generate actomyosin arcs when interacting with membrane-associated antigen in the presence of adhesion molecules expressed on professional antigen-presenting cells. In contrast to T-cells, B-cells can also respond to membrane-associated antigen without the help of adhesion molecules, when engaging antigen on pathogenic cells, like bacteria, parasites, and cancer cells. While the relationship between actomyosin arcs and inner F-actin foci remains to be explored, the coordinated formation of inner F-actin foci and NMII ring-like structures revealed in our study suggests that these structures are likely the precursors of actomyosin arcs. These structures can potentially be enhanced and matured by adhesion molecule interactions between B-cells and antigen-presenting membranes.

Our findings suggest an increase in the molecular density within BCR clusters or B-cell synapses as one of the mechanisms by which B-cell contraction promotes BCR signaling attenuation. During contraction, the molecular density of individual BCR clusters, measured by their MFI and peak FI of BCR clustered Fab’, increased faster than during the spreading and post-contraction phases. Surprisingly, increases in molecular density induced disassociation of both the stimulatory kinase Syk and the inhibitory phosphatase SHIP-1, contradicting the existing dogma of sequential association of stimulatory and inhibitory signaling molecules with the BCR (Franks and Cambier 2018). Interestingly, the disassociation of SHIP-1 is much more sensitive to BCR molecular density than Syk disassociation. Syk does not disassociate until the molecular density of BCR clusters reaches the top 10% range, while SHIP-1 disassociates from BCR clusters with increases over the entire detectable range of molecular densities. When B-cell contraction is inhibited, the molecular density of BCR clusters is reduced to a range with limited Syk disassociation and normal SHIP-1 disassociation, probably resulting in high Syk to SHIP-1 molecular ratios in BCR clusters than contracting B-cells, increasing BCR signaling levels. The consistency of the data from AF546-Fab’ and pSyk or pSHIP-1 clusters supports this notion. However, the resolution of our widefield TIRF imaging limited our ability to examine nascent BCR clusters that actively recruit signaling molecules. Available antibodies did not allow us to simultaneously stain Syk and SHIP-1 or their phosphorylated forms and determine their relative levels in the same cluster. The timing and dynamics of Syk and SHIP-1 recruitment to individual BCR clusters and the direct relationship between Syk and SHIP-1 association and disassociation with BCR clusters and their phosphorylation remain to be further investigated.

How the molecular density within BCR clusters promotes disassociation of signaling molecules is unknown. We speculate that molecular crowding may displace signaling molecules out of BCR clusters. Supporting this possibility, disassociation of the 145 kDa SHIP-1 is likely to be more sensitive to changes in the molecular density of BCR clusters, compared to disassociation of the 72 kDa Syk. However, these hypotheses need to be further examined. An interesting finding of this study is that the pCD79a and pSyk levels were higher in individual BCR clusters of cNKO B-cells than those of flox control B-cells, even when BCR clusters had similar molecular densities. These data suggest additional mechanisms for B-cell contraction to promote BCR signaling attenuation. In addition to increasing molecular density within BCR clusters, the contractile forces generated by actomyosin rings on the B-cell membrane and BCR clusters may cause changes to the conformations of both BCRs and associated signaling molecules and their lateral interactions in the membrane. These changes may favor the disassociation rather than the association of signaling molecules with BCR clusters. Recently solved molecular assembly structures of both human and mouse BCRs (Dong et al. 2022; Su et al. 2022) support conformational and lateral molecular interaction changes as possible mechanisms for BCR signaling regulation. Similar to the differential impact of the molecular density on the disassociation of Syk and SHIP-1 from BCR clusters, B-cell contraction may differentially affect the interaction of surface BCRs with cytoplasmic and membrane-anchored signaling molecules, such as the lipidated and lipid raft-resident Src kinase Lyn that is responsible for phosphorylating both the immunoreceptor tyrosine-based activation motif (ITAM) of CD79a and the immunoreceptor tyrosine-based inhibitory motif (ITIM) that SHIP-1 binds to (Franks and Cambier 2018).

Following antigen-induced BCR signaling at immunological synapses, B-cells internalize BCR-captured antigen for processing and presentation. Actomyosin is required for BCR-mediated endocytosis of antigen, particularly surface- and membrane-associated antigen (Natkanski et al. 2013; Hoogeboom et al. 2018; Maeda et al. 2021). NMII-mediated traction forces pull BCR-bound antigen off presenting surfaces for endocytosis in an affinity-dependent manner. We have previously shown that when antigens are tightly attached to a surface, high-affinity binding of the BCR to antigens tears the B-cell membrane in an NMII-dependent manner, which triggers lysosome exocytosis and lysosomal enzyme-mediated cleavages of antigen from the associated surface, allowing antigen endocytosis (Maeda et al. 2021). While actomyosin plays essential roles in both B-cell contraction and the subsequent antigen endocytosis, whether the actomyosin structure responsible for B-cell contraction also mediates BCR endocytosis remains an interesting and open question. Our early finding that N-WASP is required for BCR endocytosis (Liu et al. 2013a) supports this notion. BCR endocytosis can reduce B-cell surface signaling by removing the BCR from the cell surface, transitioning the BCR into an intracellular signaling state (Chaturvedi et al. 2008).

The results presented here have revealed novel insights into the mechanisms underlying actin-facilitated signaling attenuation of the BCR. Taking the previous and current data of our and other labs together, we propose a new working model for such actin-mediated signaling downregulation (Figure 10). Upon encountering membrane-associated antigen, such as antigen presented by follicular dendritic cells and on the surfaces of pathogens, mature follicular B-cells undergo rapid spreading, primarily driven by WASP-mediated branched actin polymerization, which maximizes B-cell contact with antigen-presenting surfaces and BCR-antigen engagement, amplifying signaling. Following maximal spreading, N-WASP distal to lamellipodial networks activates Arp2/3-mediated branched actin polymerization, which initiates the formation of inner F-actin foci from lamellipodia towards the center of the B-cell contact zone (Figure 10). NMII is then preferentially recruited to these relatively stable inner foci, which promotes the centripetal movement of inner F-actin foci and the maturation of ring-like actomyosin structures, enabling B-cell contraction. B-cell contraction pushes the BCR microclusters formed during B-cell spreading to the center of the contact zone, increasing their molecular density. Increased molecular density promotes the disassociation of signaling molecules from BCR clusters, probably due to crowding and conformational changes, leading to signal downregulation (Figure 10). Inhibitory signaling molecules likely activate the actin reorganization that drives B-cell contraction by promoting the activation and recruitment of NMII to the B-cell contact zone (Liu et al. 2013a; Seeley-Fallen et al. 2022) by hitherto unknown mechanisms. The actomyosin structures responsible for B-cell contraction may further drive B-cells to internalize engaged antigen, further downregulating signaling at the B-cell surface and initiating antigen processing and presentation. Thus, actin reorganization downstream of inhibitory phosphatases reinforces signaling attenuation by driving B-cell contraction.

A working model for cell traction-mediated BCR signaling attenuation.

When encountering membrane-associated antigen, mature follicular B-cells undergo rapid spreading, primarily driven by WASP-mediated branched actin polymerization, which maximizes B-cell contact with antigen-presenting surface and BCR-antigen engagement, amplifying signaling. Upon reaching maximal spreading, N-WASP distal to lamellipodial networks activates Arp2/3-mediated branched actin polymerization, which initiates the generation of inner F-actin foci from lamellipodia towards the center of the B-cell contact zone. NMII is then preferentially recruited to these relatively stable inner foci, which in turn promotes the centripetal movement of inner F-actin foci and the maturation of ring-like actomyosin structures, enabling B-cell contraction. B-cell contraction pushes the BCR microclusters formed during B-cell spreading to the center of the contact zone, increasing their molecular density. Increased molecular density promotes the disassociation of signaling molecules from BCR clusters, probably due to crowding and conformational changes, leading to signaling attenuation.

Materials and Methods

Key Reagents Table

Mice and B-cell isolation

Wild-type (WT) C57BL/6 mice and WASP knockout (WKO) mice on the C57BL/6 background were purchased from Jackson Laboratories. C57BL/6 mice expressing LifeAct-GFP transgene (Riedl et al. 2010) were kindly provided by Dr. Roberto Weigert at National Cancer Institute, USA. C57BL/6 mice expressing the LifeAct-RFP transgene were kindly provided by Dr. Klaus Ley at La Jolla Institute for Allergy & Immunology. C57BL/6 mice expressing the GFP-non-muscle myosin IIA (NMIIA) transgene were kindly provided by Dr. Robert Adelstein at the National Heart, Lung, and Blood Institute, USA. WKO mice were bred with LifeAct-GFP mice to obtain LifeAct-GFP-expressing WKO mice. GFP-NMIIA mice were crossed with LifeAct-RFP mice to generate mice expressing both transgenes. N-WASPflox/flox on a 129Sv background (Cotta-de-Almeida et al. 2007) were kindly provided by Dr. Lisa Westerberg at Karolinska Institute, Sweden. B-cell-specific N-WASP knockout mice (cNKO, CD19Cre/+N-WASPflox/flox) and floxed littermate controls (N-WASPflox/flox) were obtained by breeding N-WASPflox/flox mice with CD19Cre/+ mice on a C57BL/6 background.

Primary B-cells were isolated from the spleens of 6 to 18 week-old male or female mice, using a previously published protocol (Sharma et al. 2009). Briefly, mononuclear cells were isolated by Ficoll density-gradient centrifugation (Millipore Sigma), and T-cells were eliminated by complement-mediated cytolysis with anti-mouse CD90.2 mAb (BD Biosciences) and guinea pig complement (Innovative Research Inc). Monocytes and dendritic cells were eliminated by panning at 37°C and 5% CO2. Isolated B-cells were kept on ice in DMEM (Lonza) supplemented with 0.6% BSA (Thermo Fisher Scientific). All work involving mice was approved by the Institutional Animal Care and Usage Committee of the University of Maryland.

Pseudo-antigen-coated planar lipid bilayers

Planar lipid bilayers (PLB) were prepared using a previously described method (Dustin et al. 2007; Liu et al. 2012a). Briefly, liposomes were generated from a mixture of 5 mM (total concentration) 1,2-dioleoyl-sn-glycero-3-phosphocholine and 1,2-dioleoyl-sn-glycero-3-phosphoethanolamine-cap-biotin (Avanti Polar Lipids) at a 100:1 molar ratio by sonication. Glass coverslips, cleaned overnight with Piranha solution (KMG chemicals), were attached to 8-well chambers (Lab-Tek) and incubated with liposomes (0.05 mM) in PBS for 20 min at room temperature and washed with PBS. The chambers were then incubated with 1 µg/ml streptavidin (Jackson ImmunoResearch Laboratories) for 10 min, washed with PBS, and then incubated with 10 µg/ml mono-biotinylated Fab’ fragment of goat anti-mouse Ig(G+M) (pseudo-antigen) (Fab’-PLB) for 10 min, followed by PBS wash. For transferrin-coated PLB (Tf-PLB), 16 16 µg/ml biotinylated holoTF was used. To visualize Fab’ clustering, a mixture of 0.5 µg/ml Alexa Fluor (AF) 546-labeled and 9.5 µg/ml unlabeled mono-biotinylated Fab’ fragment of goat anti-mouse Ig(G+M) was used. The lateral mobility of AF546-Fab’ on the PLB was tested using fluorescence recovery after photobleaching (FRAP) to ensure ≥85% AF546 fluorescence recovery within 1 min after photobleaching using a Zeiss LSM 710 equipped with a 60X oil-immersion objective.

Mono-biotinylated Fab’ fragments were generated as previously described (Liu et al. 2011). Briefly, the disulfide bond linking the two Fab fragments of F(ab’)2 goat anti-mouse Ig(G+M) was reduced using 2-mercaptoethylamine HCL (Thermo Fisher Scientific) and biotinylated by using maleimide-PEG2-biotin (Thermo Fisher Scientific). Mono-biotinylated Fab’ fragments of goat anti-mouse Ig(G+M) were labeled with AF546 using an Alexa Fluor 546 antibody labeling kit (Thermo Fisher Scientific). The molar ratio of AF546 to Fab’ in the AF546-labeled Fab’ was ∼2 determined by a Nanodrop spectrophotometer (Nanodrop Technologies).

Total internal fluorescence microscopy

To visualize molecules proximal to interacting sites between B-cells and Fab’-or Tf-PLB, we utilized total internal reflection fluorescence microscopy (TIRF) and interference reflection microscopy (IRM). Images were acquired using a Nikon TIRF system on an inverted microscope (Nikon TE2000-PFS, Nikon Instruments Inc.) equipped with a 60X, NA 1.49 Apochromat TIRF objective (Nikon), a Coolsnap HQ2 CCD camera (Roper Scientific), and two solid-state lasers of wavelength 491 and 561 nm. IRM, AF488, and AF546 images were acquired sequentially.

The plasma membrane area of B-cells contacting PLB was determined using IRM images and custom MATLAB codes. Whether a B-cell contracted or not was determined using the area versus time plots, wherein if a B-cell’s contact zone area reduced by ≥5% for at least 10 sec after reaching a maximum value, it was classified as contracting. To image intracellular molecules, B-cells were incubated with Fab’-PLBs for varying lengths of time in PBS at 37°C, fixed with 4% paraformaldehyde, permeabilized with 0.05% saponin, and stained for various molecules. For live-cell imaging, B-cells were pre-warmed to 37°C and imaged as soon as B-cells were dropped into coverslip chambers coated with Fab’-PLB containing PBS in a humidity chamber at 37°C, at 2 sec per frame, up to 7 min. All images from multiple independent experiments were analyzed using NIH ImageJ and custom MatLab scripts. Acquired fluorescence intensity (FI) data were normalized to the one with the lowest FI.

Inhibitors

CK-666 (50 µM, Millipore Sigma) was used to perturb Arp2/3 activity (Nolen et al. 2009), and its non-functional derivative CK-689 (50 µM, Millipore Sigma) as a control. CK-666 or CK-689 was added at either 0 min, the start of incubation with Fab’-PLB, or at 2 min when most B-cells reached maximum spreading. Notably, B-cells take approximately 1 to 1.5 min to land on PLB. The time when B-cells were added to Fab’-PLB is referred to as 0 min, and the time when B-cells landed on PLB as the start of spreading. The effectiveness of CK-666 was determined by its inhibitory effects on the recruitment of Arp2/3, stained by an anti-Arp2 antibody (Abcam), to the B-cell contact zone using TIRF (Figure 1-figure supplement 2). Wiskostatin (Wisko, 10 µM, Millipore Sigma) was used to perturb N-WASP activity in B-cells (Peterson et al. 2004), with DMSO used as a vehicle control. Splenic B-cells were pretreated with Wisko for 10 min at 37°C before and during incubation with Fab’-PLB. The effectiveness of Wisko was determined by its inhibitory effects on the level of phosphorylated N-WASP in the B-cell contact zone using immunostaining and TIRF (Figure 1-figure supplement 4A and C). Possible effects of Wisko on WASP activation were evaluated by measuring the mean fluorescence intensity (MFI) of phosphorylated WASP in the contact zone of B-cells treated with or without Wisko for 10 min (Figure 1-figure supplement 4B and D). Blebbistatin (Bleb, 50 µM, Cayman Chemicals) was used to inhibit the NMII motor activity (Seeley-Fallen et al. 2022). Splenic B-cells were pretreated with Bleb for 20 min before and during incubation with Fab’-PLB.

Analysis of the actin cytoskeleton

F-actin was visualized by phalloidin staining in fixed cells and by LifeAct-GFP or LifeAct-RFP expressed by primary B-cells from transgenic mice in live cells. Inner F-actin foci, visualized by both phalloidin staining and LifeAct-GFP, were identified using NIH ImageJ based on the following three criteria: 1) ≥250 nm in diameter, 2) peak fluorescence intensity (FI) ≥2 fold higher than the FI of a nearby area containing no foci, and 3) ≥1 µm away from the outer edge of the B-cell contact zone. The horizontal or vertical length of a focus was measured, and the lesser of the two values was used as its diameter. To analyze the spatiotemporal relationship between inner F-actin foci and the lamellipodial F-actin network, we generated 8 radially and equally spaced kymographs from each cell using time-lapse images and MATLAB. Each kymograph was either classified as contracting or not contracting based on the movement of the leading edge of the B-cell contact zone. The percentage of 8 kymographs from each cell exhibiting inner F-actin foci that could be traced back to lamellipodial F-actin when the B-cell switched from spreading to contraction was determined.

The relative speeds and lifetimes of F-actin foci were determined using three kymographs from each B-cell (positioned to track as many inner F-actin foci as possible) and F-actin foci emerging during a 60-sec window right after B-cell maximal spreading. Only those remaining visible in individual kymographs for at least 4 sec were analyzed. The time duration of each F-actin focus detected in a kymograph was used to determine the relative lifetime. The distances individual F-actin foci moved during their lifetimes were used to determine the relative speed. The term ‘relative’ has been used because the disappearance of an F-actin focus could be due to its movement away from the region used for the kymograph or vertically from the TIRF evanescent field of excitation.

To determine the rate of myosin recruitment, GFP-NMIIA MFI in the B-cell contact zone was plotted over time, and the slope for the initial segment of the MFI versus the time plot was determined using linear regression. The percentage of B-cells with the NMIIA ring was determined by visual inspection.

Analysis of BCR-Fab’ clusters

BCR clusters were identified by clustering of AF546-Fab’ on PLBs using custom code by MATLAB. We utilized the median FI of the Fab’-PLB within the same area outside but near the B-cell contact zone as the background. The median, but not mean FI value, was used for background FI calculations to minimize fluctuations due to debris. To ensure that individual clusters with varying FI were detected as distinct objects, we used 16 graded thresholds from 1.1 to 4.1 fold of the background (0.2 fold apart) to acquire 16 sets of binary masks for each frame of time-lapse images from each cell. When clusters were detected by multiple thresholds at the same location, only the one identified by the highest threshold was retained. Objects that were smaller than 250 nm in diameter or could not be tracked for at least 20 sec were eliminated. This allowed us to detect the position of BCR-Fab’ clusters and track them over time until they merged with other clusters. The horizontal or vertical length of a focus was measured, and the lesser of the two values was used as its diameter. We chose the peak FI as a metric for the extent of Fab’ clustering by the BCR, because it does not rely on the area occupied by each cluster. The rate of peak FI increase was determined by linear regression of peak FI versus time curves for each cluster for a given window of time.

BCR signaling

Splenic B-cells were incubated with AF546-Fab’-PLB at 37°C and fixed at 1, 3, 5, 7, and 9 min. After fixation, cells were stained for phosphorylated CD79a (pCD79a, Y182) (Cell Signaling Technology), Syk (pSyk, Y519/520) (Cell Signaling Technology), SHIP-1 (pSHIP-1, Y1020) (Cell Signaling Technology), or total Syk or SHIP-1 proteins (Thermo Fisher Scientific). We identified BCR-Fab’ clusters as described. We determined the peak FI of AF546-Fab’ and the MFI of AF546-Fab’, pCD79a, pSyk, pSHIP-1, Syk, or SHIP-1 within each cluster. The ratio of pCD79a MFI to AF546-Fab’ MFI in the same cluster was used to estimate the relative phosphorylation level of BCRs in that cluster. This MFI ratio was plotted against AF546-Fab’ peak FI to analyze the relationship between BCR phosphorylation and BCR density of individual clusters. We calculated the MFI ratio of Syk to Fab’ or SHIP-1 to Fab’ in individual clusters to estimate the relative recruitment level of Syk or SHIP-1 to BCR clusters. We plotted these MFI ratios against Fab’ peak FI to determine the relationship between Syk and SHIP-1 recruitment levels and BCR density in individual clusters. We calculated the MFI ratio of pSyk to Fab’ or pSHIP-1 to Fab’ to estimate the amount of pSyk or pSHIP-1 relative to BCR in individual clusters. We plotted these MFI ratios against Fab’ peak FI to determine the relationship between Syk or SHIP-1 phosphorylation and BCR density in individual clusters. We identified pSyk or pSHIP-1 puncta using the criteria: ≥1.3 fold of the background staining outside the B-cell contact zone and ≥250 nm in diameter. We calculated the MFI ratio of pSyk to Fab’ or pSHIP-1 to Fab’ in individual puncta to estimate the amount of pSyk or pSHIP-1 relative to BCR in individual puncta. We plotted these MFI ratios against Fab’ peak FI to determine the relationship between Syk or SHIP-1 phosphorylation and BCR density in individual puncta. We determined the fraction of clusters with graded increases in Fab’ peak FI (every 20 FI units) out of the total to analyze the distribution of clusters with different Fab’ peak FI. We also determine the average MFI ratios of pCD79a, Syk, pSyk, SHIP-1, and pSHIP-1 relative to Fab’ in each graded cluster population. We further divided AF546-Fab’ clusters into three populations based on their peak AF546-Fab’ FI, relatively low (<190), medium (190-280), and high (>280, detected only in contracted cells) and compared the MFI ratios of pCD79a, pSyk, pSHIP-1, Syk, and SHIP-1 relatively to AF546-Fab’ among the three populations using statistical analysis described below. The data were generated from 3 independent experiments with 20∼23 (60∼69 total) cells and 125∼140 individual clusters (1500∼1680 total) per condition, per time point, and per experiment.

Statistical analysis

Statistical analysis was performed using the Mann-Whitney U non-parametric test for unpaired groups having different sample sizes or the Student’s t-test for paired groups with the same sample size. To compare curves, Kolmogorov-Smirnov test was used. Statistical analyses were performed in Microsoft Excel, GraphPad Prism, and MATLAB. All data are presented as mean ± SEM (standard error of the mean). When testing multiple hypotheses, p--values acquired using t-tests were corrected using the Benjamini-Hochberg/Yekutieli method for false discovery rate control.

MATLAB scripts

All MATLAB scripts used for this study are available as supplemental materials.

Supporting information